### 2017-01-26 papers/outline.tex
Adds paper outline

\documentclass{article}

\title{Progtran Paper Outline}
\date{01-26-2017}
\author{Lucas Saldyt}

\begin{document}

\maketitle
\pagenumbering{gobble}
\newpage
\pagenumbering{arabic}

\section{Abstract}
Progtran is an attempt to build a multi-language source-to-source compiler. Ideally, one will be able to convert programs in one language to programs in another without a loss in readability. This will allows for more user flexibility. For example, Python syntax is generally easier to understand than C++'s, but if one can translate Python to C++, then one can have both benefits. Progtran is an investigation into the feasibility of such conversions.
\section{Introduction}
\section{Methods}
\subsection{Grammars}
\subsection{Constructors}
\subsection{AST Transformations}
\section{Results}

\end{document}

### 2017-01-27 demo.py
Adds better value semantics

@@ -177,8 +177,8 @@ def main():
     else:
         verbosity = 1
 
-    #transpile(demoname, demos, verbosity, True)
-    transpile(demoname, demos, verbosity, runlang=False)
+    transpile(demoname, demos, verbosity, True)
+    #transpile(demoname, demos, verbosity, runlang=False)
 
 
 if __name__ == '__main__':

### 2017-01-27 examples/output/test_output/main.py

@@ -3,208 +3,95 @@ from __future__ import division
 from __future__ import print_function
 from __future__ import unicode_literals
 from past.utils import old_div
+from __pylib__  import *
 from sys import * 
-from string import * 
-import random as rd 
-from functions import * 
-dictionary = dict() 
-iterations = 0 
-interactive = False 
-moveAhead = 0 
-quit = False 
-seed = rd.randint(0,1000000) 
-def usage (): 
-    """rint out information regarding how to use this particular program."""  
-def loadIntoDictionary (argv,dictionary): 
-    """arse the argv array to a dictionary of strings->strings or 
-    
-        strings->string arrays. We assume all flags begin with a hyphen and all
-    
-        arguments to flags do not. So if we see -abc 1 2 3 then in the 
-    
-        dictionary we will get: dict['abc'] = ['1','2','3']
-    
-        """
+import random as r 
+sys.path.append("../random") 
+import randomWeighted as rw 
+class WordNode():
+    def __init__ (self): 
+        self.incoming = [] 
+        self.outgoing = dict() 
+        self.count = 1  
+    def addIncoming (self,word): 
+        if (not word in self.incoming): 
+            self.incoming.append(word) 
+         
     """
-        limit = len(argv)
+        def addOutgoing(self, word):
     
-        i = 0
+            if word in self.outgoing.keys():
     
-        while i < limit:
-    
-            if argv[i].startswith('-'):
-    
-                j = i+1
-    
-                temp = []
-    
-                while j < limit and not argv[j].startswith('-'):
-    
-                    temp.append(argv[j])
-    
-                    j += 1
-    
-    end
-                if len(temp) == 1:
-    
-                    dictionary[argv[i]] = temp[0]
-    
-    end
-                elif len(temp) > 1:
-    
-                    dictionary[argv[i]] = temp
-    
-    end
-                else:
-    
-                    print ('ERROR: Every input beginning with '+
-    
-                    '"-" should take at least one argument. "'+
-    
-                    argv[i]+'". Has no such argument.\n')
-    
-                    usage()
-    
-                    sys.exit()
-    
-    end
-                i = j-1
-    
-    end
-            i += 1
-    
-    end
-        return dictionary
-    
-        """  
-def parseInput (argv): 
-    """This is important for if you're interacting with the program through"""
-    """the python interpreter or something. Don't ask me.""" 
-    """
-        if argv is None:
-    
-            argv = sys.argv
-    
-    end
[…]

### 2017-01-27 examples/test/main.py

@@ -1,0 +1,54 @@
+import sys
+import random as r
+sys.path.append('../random')
+import randomWeighted as rw
+
+class WordNode():
+    def __init__(self):
+        self.incoming = []
+        self.outgoing = dict()
+        self.count = 1
+
+    """
+
+    def addIncoming(self, word):
+        if not word in self.incoming:
+            self.incoming.append(word)
+
+    def addOutgoing(self, word):
+        if word in self.outgoing.keys():
+            self.outgoing[word] += 1
+        else:
+            self.outgoing[word] = 1
+    def incrementCount(self):
+        self.count += 1
+
+    def getNextWordUniform(self):
+        rand = r.randint(0, len(self.outgoing.keys())-1)
+        key = self.outgoing.keys()[rand]
+        return key
+
+    def getNextWordDeterministic(self):
+        heaviest = []
+        weight = 0
+        for key in self.outgoing.keys():
+            if self.outgoing[key] > weight:
+                weight = self.outgoing[key]
+                heaviest = [key]
+            elif self.outgoing[key] == weight:
+                heaviest.append(key)
+        key = heaviest[0]
+        if len(heaviest) > 1:
+            key = heaviest[r.randint(0, len(heaviest)-1)]
+        return key
+
+    def getNextWordWeighted(self):
+        #TODO it might save time to store this permanently and only update it when new outgoing edges are added. For now don't worry about such things.
+        weights = []
+        for key in self.outgoing.keys():
+            weights.append(self.outgoing[key])
+        randgen = rw.WeightedRandomGenerator(weights)
+        key = self.outgoing.keys()[randgen.next()]
+        return key
+    """
+

### 2017-01-27 examples/value/main.py

@@ -1,0 +1,5 @@
+
+
+if __name__ == "__main__":
+    a = self.outgoing[word]
+    self.outgoing[word] += "b"

### 2017-01-27 examples/output/test_output/main.py
Adds better boolean semantics

@@ -12,12 +12,16 @@ class WordNode():
     def __init__ (self): 
         self.incoming = [] 
         self.outgoing = dict() 
-        self.count = 1  
-    def addIncoming (self,word): 
-        if (not word in self.incoming): 
-            self.incoming.append(word) 
-         
+        self.count = 1 
     """
+        def addIncoming(self, word):
+    
+            if not word in self.incoming:
+    
+                self.incoming.append(word)
+    
+    end
+    end
         def addOutgoing(self, word):
     
             if word in self.outgoing.keys():

### 2017-01-27 examples/output/test_output/main.py
Adds full porting functionality for wordnode.py

@@ -12,90 +12,39 @@ class WordNode():
     def __init__ (self): 
         self.incoming = [] 
         self.outgoing = dict() 
-        self.count = 1 
-    """
-        def addIncoming(self, word):
-    
-            if not word in self.incoming:
-    
-                self.incoming.append(word)
-    
-    end
-    end
-        def addOutgoing(self, word):
-    
-            if word in self.outgoing.keys():
-    
-                self.outgoing[word] += 1
-    
-    end
-            else:
-    
-                self.outgoing[word] = 1
-    
-    end
-    end
-        def incrementCount(self):
-    
-            self.count += 1
-    
-    end
-        def getNextWordUniform(self):
-    
-            rand = r.randint(0, len(self.outgoing.keys())-1)
-    
-            key = self.outgoing.keys()[rand]
-    
-            return key
-    
-    end
-        def getNextWordDeterministic(self):
-    
-            heaviest = []
-    
-            weight = 0
-    
-            for key in self.outgoing.keys():
-    
-                if self.outgoing[key] > weight:
-    
-                    weight = self.outgoing[key]
-    
-                    heaviest = [key]
-    
-    end
-                elif self.outgoing[key] == weight:
-    
-                    heaviest.append(key)
-    
-    end
-    end
-            key = heaviest[0]
-    
-            if len(heaviest) > 1:
-    
-                key = heaviest[r.randint(0, len(heaviest)-1)]
-    
-    end
-            return key
-    
-    end
-        def getNextWordWeighted(self):
-    
-            #TODO it might save time to store this permanently and only update it when new outgoing edges are added. For now don't worry about such things.
-    
-            weights = []
-    
-            for key in self.outgoing.keys():
-    
-                weights.append(self.outgoing[key])
-    
-    end
-            randgen = rw.WeightedRandomGenerator(weights)
-    
-            key = self.outgoing.keys()[randgen.next()]
-    
-            return key
-    
-    end
-        """  
+        self.count = 1  
+    def addIncoming (self,word): 
+        if (not word in self.incoming): 
+            self.incoming.append(word) 
+          
+    def addOutgoing (self,word): 
+        if (word in self.outgoing.keys()): 
+            self.outgoing[word] += 1 
+          
+    def incrementCount (self): 
+        self.count += 1  
+    def getNextWordUniform (self): 
+        rand = r.randint(0,len(self.outgoing.keys()) - 1) 
[…]

### 2017-01-27 examples/test/main.py

@@ -1,54 +1,81 @@
-import sys
-import random as r
-sys.path.append('../random')
-import randomWeighted as rw
+import obj_word
+import string
 
-class WordNode():
-    def __init__(self):
-        self.incoming = []
-        self.outgoing = dict()
-        self.count = 1
+class WordList():
+    '''WordList uses words as keys and a list of values as the value. The list has words that follow the word used as the key. This can then be used to create automatically generated sentences. I'm also keeping raw counts of words to see what may be over used.'''
+    def __init__(self, limit=20):
+        self.wordlist = dict()
+        #Add period to the word list.
+        self.wordlist['.'] = obj_word.WordNode()
 
-    """
+        self.sentenceLengthLimit=limit
 
-    def addIncoming(self, word):
-        if not word in self.incoming:
-            self.incoming.append(word)
+        self.currentWord = '.'
 
-    def addOutgoing(self, word):
-        if word in self.outgoing.keys():
-            self.outgoing[word] += 1
+
+    def addWords(self, words):
+        previous_word = '.'
+        for i in xrange(len(words)):
+            w = words[i]
+            try:
+                self.wordlist[w].incrementCount()
+            except KeyError:
+                self.wordlist[w] = obj_word.WordNode()
+            #If there is a previous word.
+            if i != 0:
+                #Add this word as outgoing from the previous word.
+                self.wordlist[previous_word].addOutgoing(w)
+                #Add the previous word as incoming to this word.
+                self.wordlist[w].addIncoming(previous_word)
+            else:
+                #Add period as outgoing to this word to 
+                #indicate that this word can begin a sentence.
+                self.wordlist['.'].addOutgoing(w)
+                self.wordlist[w].addIncoming('.')
+            previous_word = w
+        #If the very last word is not a period, it should be
+        if previous_word != '.':
+            self.wordlist[previous_word].addOutgoing('.')
+            self.wordlist['.'].addIncoming(previous_word)
+
+    def getNextWord(self, howToGet):
+        if howToGet == 'd':
+            self.currentWord = self.wordlist[self.currentWord]\
+            .getNextWordDeterministic()
+        elif howToGet == 'w':
+            self.currentWord = self.wordlist[self.currentWord]\
+            .getNextWordWeighted()
+        elif howToGet == 'u':
+            self.currentWord = self.wordlist[self.currentWord]\
[…]

### 2017-01-27 examples/value/main.py

@@ -3,3 +3,4 @@
 if __name__ == "__main__":
     a = self.outgoing[word]
     self.outgoing[word] += "b"
+    key = heaviest[r.randint(0, len(heaviest)-1)]

### 2017-01-27 examples/output/test_output/main.py
Fixes trycatch, continues extending value semantics

@@ -4,47 +4,143 @@ from __future__ import print_function
 from __future__ import unicode_literals
 from past.utils import old_div
 from __pylib__  import *
-from sys import * 
-import random as r 
-sys.path.append("../random") 
-import randomWeighted as rw 
-class WordNode():
-    def __init__ (self): 
-        self.incoming = [] 
-        self.outgoing = dict() 
-        self.count = 1  
-    def addIncoming (self,word): 
-        if (not word in self.incoming): 
-            self.incoming.append(word) 
-          
-    def addOutgoing (self,word): 
-        if (word in self.outgoing.keys()): 
-            self.outgoing[word] += 1 
-          
-    def incrementCount (self): 
-        self.count += 1  
-    def getNextWordUniform (self): 
-        rand = r.randint(0,len(self.outgoing.keys()) - 1) 
-        key = self.outgoing.keys()[rand] 
-        return key  
-    def getNextWordDeterministic (self): 
-        heaviest = [] 
-        weight = 0 
-        for key in self.outgoing.keys(): 
-            if (self.outgoing[key] > weight): 
-                weight = self.outgoing[key] 
-                heaviest = [key] 
-            elif self.outgoing[key] == weight:
-                heaviest.append(key)   
-        key = heaviest[0] 
-        if (len(heaviest) > 1): 
-            key = heaviest[r.randint(0,len(heaviest) - 1)] 
-         
-        return key  
-    def getNextWordWeighted (self): 
-        weights = [] 
-        for key in self.outgoing.keys(): 
-            weights.append(self.outgoing[key])  
-        randgen = rw.WeightedRandomGenerator(weights) 
-        key = self.outgoing.keys()[randgen.next()] 
-        return key   
+from obj_word import * 
+from string import * 
+class WordList():
+    def __init__ (self,limit=20): 
+        self.wordlist = dict()
+        """Add period to the word list.""" 
+        self.wordlist["."] = obj_word.WordNode() 
+        self.sentenceLengthLimit = limit 
+        self.currentWord = "."  
+    def addWords (self,words): 
+        previous_word = "." 
+        for i in range(len(words)): 
+            w = words[i] 
+            try:
+            
+                self.wordlist[w].incrementCount() 
+            
+            except KeyError: 
+                self.wordlist[w] = obj_word.WordNode()   
+    """
+                #If there is a previous word.
+    
+                if i != 0:
+    
+                    #Add this word as outgoing from the previous word.
+    
+                    self.wordlist[previous_word].addOutgoing(w)
[…]

### 2017-01-27 examples/test/main.py

@@ -2,7 +2,6 @@ import obj_word
 import string
 
 class WordList():
-    '''WordList uses words as keys and a list of values as the value. The list has words that follow the word used as the key. This can then be used to create automatically generated sentences. I'm also keeping raw counts of words to see what may be over used.'''
     def __init__(self, limit=20):
         self.wordlist = dict()
         #Add period to the word list.
@@ -21,6 +20,7 @@ class WordList():
                 self.wordlist[w].incrementCount()
             except KeyError:
                 self.wordlist[w] = obj_word.WordNode()
+    """
             #If there is a previous word.
             if i != 0:
                 #Add this word as outgoing from the previous word.
@@ -79,3 +79,4 @@ class WordList():
         s = sorted(self.wordlist.keys(), key=lambda word: self.wordlist[word].count)
         for word in s:
             print word+' - '+str(self.wordlist[word].count)
+    """

### 2017-01-27 examples/value/main.py

@@ -4,3 +4,4 @@ if __name__ == "__main__":
     a = self.outgoing[word]
     self.outgoing[word] += "b"
     key = heaviest[r.randint(0, len(heaviest)-1)]
+    self.wordlist[w].incrementCount()

### 2017-01-27 examples/output/test_output/main.py
Adds lambdas

@@ -22,125 +22,47 @@ class WordList():
                 self.wordlist[w].incrementCount() 
             
             except KeyError: 
-                self.wordlist[w] = obj_word.WordNode()   
-    """
-                #If there is a previous word.
-    
-                if i != 0:
-    
-                    #Add this word as outgoing from the previous word.
-    
-                    self.wordlist[previous_word].addOutgoing(w)
-    
-                    #Add the previous word as incoming to this word.
-    
-                    self.wordlist[w].addIncoming(previous_word)
-    
-    end
-                else:
-    
-                    #Add period as outgoing to this word to 
-    
-                    #indicate that this word can begin a sentence.
-    
-                    self.wordlist['.'].addOutgoing(w)
-    
-                    self.wordlist[w].addIncoming('.')
-    
-    end
-                previous_word = w
-    
-    end
-            #If the very last word is not a period, it should be
-    
-            if previous_word != '.':
-    
-                self.wordlist[previous_word].addOutgoing('.')
-    
-                self.wordlist['.'].addIncoming(previous_word)
-    
-    end
-    end
-        def getNextWord(self, howToGet):
-    
-            if howToGet == 'd':
-    
-                self.currentWord = self.wordlist[self.currentWord]\
-    
-                .getNextWordDeterministic()
-    
-    end
-            elif howToGet == 'w':
-    
-                self.currentWord = self.wordlist[self.currentWord]\
-    
-                .getNextWordWeighted()
-    
-    end
-            elif howToGet == 'u':
-    
-                self.currentWord = self.wordlist[self.currentWord]\
-    
-                .getNextWordUniform()
-    
-    end
-            else:
-    
-                print 'ERROR in obj_wordlist.py.'; exit()
-    
-    end
-            return self.currentWord
-    
-    end
-        def getSentence(self, howToGet, sentence_type):
-    
-            print '\nA '+sentence_type+' sentence: '
-    
-            word = self.getNextWord(howToGet)
-    
-            sentence = string.capitalize(str(word)+' ')
-    
-            count = 0
-    
-            while word != '.' and count < self.sentenceLengthLimit:
-    
-                word = self.getNextWord(howToGet)
-    
-                sentence += word+' '
-    
-                count+=1
-    
-    end
-            print sentence
-    
-            print 'Counted to '+str(count)
-    
-            self.currentWord = '.' #Reset to sentence start.
-    
[…]

### 2017-01-27 examples/test/main.py

@@ -20,7 +20,6 @@ class WordList():
                 self.wordlist[w].incrementCount()
             except KeyError:
                 self.wordlist[w] = obj_word.WordNode()
-    """
             #If there is a previous word.
             if i != 0:
                 #Add this word as outgoing from the previous word.
@@ -76,7 +75,6 @@ class WordList():
         self.getSentence('u', 'uniform random')
 
     def getWordsByMostFrequentUsage(self):
-        s = sorted(self.wordlist.keys(), key=lambda word: self.wordlist[word].count)
+        #s = sorted(self.wordlist.keys(), key=lambda word: self.wordlist[word].count)
         for word in s:
             print word+' - '+str(self.wordlist[word].count)
-    """

### 2017-01-27 examples/value/main.py

@@ -5,3 +5,4 @@ if __name__ == "__main__":
     self.outgoing[word] += "b"
     key = heaviest[r.randint(0, len(heaviest)-1)]
     self.wordlist[w].incrementCount()
+    #s = sorted(self.wordlist.keys(), key=lambda word: self.wordlist[word].count)

### 2017-01-27 examples/output/test_output/main.py
Adds additional porting capabilities

@@ -4,65 +4,105 @@ from __future__ import print_function
 from __future__ import unicode_literals
 from past.utils import old_div
 from __pylib__  import *
-from obj_word import * 
+"""Functions and some global variables were moved here simply to clean up main.py.""" 
+from re import *
+"""import regular expressions""" 
 from string import * 
-class WordList():
-    def __init__ (self,limit=20): 
-        self.wordlist = dict()
-        """Add period to the word list.""" 
-        self.wordlist["."] = obj_word.WordNode() 
-        self.sentenceLengthLimit = limit 
-        self.currentWord = "."  
-    def addWords (self,words): 
-        previous_word = "." 
+from obj_wordlist import *
+"""Limit on the length of generated sentences.""" 
+"""TODO. Later you could do a depth-limited, depth-first search for a path to a period to end the sentence.""" 
+sentenceLengthLimit = 20
+"""Word list - store all words and connections here""" 
+wordlist = obj_wordlist.WordList()
+"""Keep track of rejected words for testing purposes""" 
+rejected_words = []
+"""For now, use a regular expression to match only words containing""" 
+"""alpha-numeric characters, hyphens, or apostrophes.""" 
+alpha = re.compile("^[\w\'-]+$")
+"""Match articles""" 
+articles = re.compile("a|an|the") 
+def processFile (filetoreadin,articlesSep): 
+    global alpha,rejected_words,articles 
+    to_return = [] 
+    file_handle = open(filetoreadin) 
+    line = file_handle.readline() 
+    article = ""
+    """This will be set if an article is found.""" 
+    while line: 
+        line = string.lower(line)
+        """lower case the whole string.""" 
+        words = line.split(" ") 
         for i in range(len(words)): 
-            w = words[i] 
-            try:
+            w = words[i]
+            """Remove white space""" 
+            w = w.strip()
+            """Deal with commas""" 
+            if (w.endswith(",")): 
+                w = w.replace(",","") 
             
-                self.wordlist[w].incrementCount() 
+            """Deal with periods""" 
+            endsWithPeriod = False 
+            if (w.endswith(".")): 
+                w = w.replace(".","") 
+                endsWithPeriod = True 
             
-            except KeyError: 
-                self.wordlist[w] = obj_word.WordNode() 
-            """If there is a previous word.""" 
-            if (i != 0): 
-                """Add this word as outgoing from the previous word.""" 
-                self.wordlist[previous_word].addOutgoing(w)
[…]

### 2017-01-27 examples/test/main.py

@@ -1,80 +1,83 @@
-import obj_word
+#Functions and some global variables were moved here simply to clean up main.py.
+
+import re #import regular expressions
 import string
-
-class WordList():
-    def __init__(self, limit=20):
-        self.wordlist = dict()
-        #Add period to the word list.
-        self.wordlist['.'] = obj_word.WordNode()
-
-        self.sentenceLengthLimit=limit
-
-        self.currentWord = '.'
+import obj_wordlist
 
 
-    def addWords(self, words):
-        previous_word = '.'
+#Limit on the length of generated sentences.
+#TODO. Later you could do a depth-limited, depth-first search for a path to a period to end the sentence.
+sentenceLengthLimit = 20
+
+
+#Word list - store all words and connections here
+wordlist = obj_wordlist.WordList()
+
+
+#Keep track of rejected words for testing purposes
+rejected_words = []
+
+
+#For now, use a regular expression to match only words containing
+#alpha-numeric characters, hyphens, or apostrophes.
+alpha = re.compile("^[\w\'-]+$")
+
+#Match articles
+articles = re.compile('a|an|the')
+
+def processFile(filetoreadin, articlesSep):
+    global alpha, rejected_words, articles
+    to_return = []
+    file_handle=open(filetoreadin)
+    line = file_handle.readline()
+    article = '' #This will be set if an article is found.
+    while line:
+        line = string.lower(line) #lower case the whole string.
+        words = line.split(' ')
         for i in xrange(len(words)):
             w = words[i]
-            try:
-                self.wordlist[w].incrementCount()
-            except KeyError:
-                self.wordlist[w] = obj_word.WordNode()
-            #If there is a previous word.
-            if i != 0:
-                #Add this word as outgoing from the previous word.
-                self.wordlist[previous_word].addOutgoing(w)
-                #Add the previous word as incoming to this word.
-                self.wordlist[w].addIncoming(previous_word)
+            #Remove white space
+            w = w.strip()
+
+            #Deal with commas
+            if w.endswith(","):
+                w = w.replace(",","")
+            #Deal with periods
+            endsWithPeriod = False
+            if w.endswith("."):
+                w = w.replace(".","")
+                endsWithPeriod = True
+
+            #for now, remove anything that is not purely alpha-numeric
+            result = alpha.match(w)
+            if result is None:
+                print("")
+            """
+                if not w in rejected_words:
+                    rejected_words.append(w)
             else:
[…]

### 2017-01-27 examples/text_prediction/functions.py

@@ -20,7 +20,7 @@ rejected_words = []
 
 #For now, use a regular expression to match only words containing
 #alpha-numeric characters, hyphens, or apostrophes.
-alpha = re.compile('^[\w\'-]+$')
+alpha = re.compile("^[\w\'-]+$")
 
 #Match articles
 articles = re.compile('a|an|the')

### 2017-01-27 examples/value/main.py

@@ -5,4 +5,5 @@ if __name__ == "__main__":
     self.outgoing[word] += "b"
     key = heaviest[r.randint(0, len(heaviest)-1)]
     self.wordlist[w].incrementCount()
-    #s = sorted(self.wordlist.keys(), key=lambda word: self.wordlist[word].count)
+    s = sorted(self.wordlist.keys(), key=lambda word: self.wordlist[word].count)
+    s = sorted(self.wordlist.keys(), key=lambda word : 0)

### 2017-01-28 examples/class/main.py
WIP

@@ -1,82 +1,2 @@
-import obj_word
-import string
 
-class WordList():
-    def __init__(self, limit=20):
-        self.wordlist = dict()
-        #Add period to the word list.
-        self.wordlist['.'] = obj_word.WordNode()
-        self.sentenceLengthLimit=limit
-        self.currentWord = '.'
-
-    def addWords(self, words):
-        previous_word = '.'
-        """
-        for i in xrange(len(words)):
-
-            w = words[i]
-            try:
-                self.wordlist[w].incrementCount()
-            except KeyError:
-                self.wordlist[w] = obj_word.WordNode()
-            #If there is a previous word.
-            if i != 0:
-                #Add this word as outgoing from the previous word.
-                self.wordlist[previous_word].addOutgoing(w)
-                #Add the previous word as incoming to this word.
-                self.wordlist[w].addIncoming(previous_word)
-            else:
-                #Add period as outgoing to this word to 
-                #indicate that this word can begin a sentence.
-                self.wordlist['.'].addOutgoing(w)
-                self.wordlist[w].addIncoming('.')
-            previous_word = w
-        #If the very last word is not a period, it should be
-        if previous_word != '.':
-            self.wordlist[previous_word].addOutgoing('.')
-            self.wordlist['.'].addIncoming(previous_word)
-        """
-    """
-
-    def getNextWord(self, howToGet):
-        if howToGet == 'd':
-            self.currentWord = self.wordlist[self.currentWord]\
-            .getNextWordDeterministic()
-        elif howToGet == 'w':
-            self.currentWord = self.wordlist[self.currentWord]\
-            .getNextWordWeighted()
-        elif howToGet == 'u':
-            self.currentWord = self.wordlist[self.currentWord]\
-            .getNextWordUniform()
-        else:
-            print 'ERROR in obj_wordlist.py.'; exit()
-        return self.currentWord
-
-
-    def getSentence(self, howToGet, sentence_type):
-        print '\nA '+sentence_type+' sentence: '
-        word = self.getNextWord(howToGet)
-        sentence = string.capitalize(str(word)+' ')
-        count = 0
-        while word != '.' and count < self.sentenceLengthLimit:
-            word = self.getNextWord(howToGet)
-            sentence += word+' '
-            count+=1
-        print sentence
-        print 'Counted to '+str(count)
-        self.currentWord = '.' #Reset to sentence start.
-
[…]

### 2017-01-28 examples/value/main.py

@@ -6,4 +6,3 @@ if __name__ == "__main__":
     key = heaviest[r.randint(0, len(heaviest)-1)]
     self.wordlist[w].incrementCount()
     s = sorted(self.wordlist.keys(), key=lambda word: self.wordlist[word].count)
-    s = sorted(self.wordlist.keys(), key=lambda word : 0)

### 2017-01-28 src/compiler.cpp

@@ -76,7 +76,7 @@ namespace compiler
             LexMapLexer(just("    "s),     "tab",        "tab",        3),
             LexMapLexer(startswith("\t"s), "tab",        "tab",        3),
             LexMapLexer(digits,            "int",        "literal",    3),
-            LexMapLexer(identifiers,       "identifier", "identifier", 3)};
+            LexMapLexer(identifiers,       "*text*",    "identifier", 3)};
 
         lexer_set.push_back(LexMapLexer(startswith(grammar.comment_delimiter), "comment", "comment", 3));
         for (auto delimiter : grammar.string_delimiters)

### 2017-01-28 src/lex/lexmap.cpp

@@ -68,6 +68,11 @@ namespace lex
      */
     tuple<Token, vector<string>> LexMap::identify(vector<string> terms) const
     {
+        string text;
+        for (auto term : terms)
+        {
+            text += term;
+        }
         // Return result of first lexer to match against remaining terms
         for (auto lexer : language_lexers)
         {
@@ -75,7 +80,9 @@ namespace lex
             if(result.result)
             {
                 //print("vector<string> identified as " + lexer.name);
-                return make_tuple(Token(result.consumed, lexer.name, lexer.type), result.remaining);
+                string type = lexer.type == "*text*" ? text
+                                                     : lexer.type;
+                return make_tuple(Token(result.consumed, lexer.name, type), result.remaining);
             }
         }
 

### 2017-01-29 papers/outline.tex
WIP paper
Adds intro, edits abstract, removes pdf

@@
 
-\title{Progtran Paper Outline}
+\usepackage{indentfirst}
+\usepackage{setspace}
+\doublespacing
+
+\title{Fully Generalized Compilation}
 \date{01-26-2017}
@@
 \section{Abstract}
-Progtran is an attempt to build a multi-language source-to-source compiler.
-Ideally, one will be able to convert programs in one language to programs in another without a loss in readability.
-This will allows for more user flexibility.
-For example, Python syntax is generally easier to understand than C++'s, but if one can translate Python to C++, then one can have both benefits.
-Progtran is an investigation into the feasibility of such conversions.
+
+Assuming that two languages are \textit{isomorphic}, one syntax can be converted to another if given an adequate description of each syntax's grammar.
+At an abstract level, this conversion is entirely practical.
+Progtran is an investigation into the feasibility of a \textbf{Fully Generalized Compiler}, a multi-language source-to-source compiler.
+Given source code in one language, a description of its grammar \textbf{A} , and a description of an output language's grammar \textbf{B}, can \textbf{A} be converted to \textbf{B} such that the output in \textbf{B} is indistinguishable from a program originally written in \textbf{B}?
+
 \section{Introduction}
+
+A \textbf{Full Generalized Compiler} is a tool for programming language researchers, providing a \textit{dynamic framework} for easily modifying syntax of input and output languages.
+The grammar of a programming language can be modified without recompiling the software.
+This is demonstrated by how easily a new programming language can be invented with Progtran.
+However, Progtran also uses this concept (dynamic syntax changes) to re-implement existing source-to-source compilation tools, such as \textbf{Cython} or \textbf{2to3}.
+
 \section{Methods}
@@
 \subsection{AST Transformations}
+
 \section{Results}

### 2017-02-02 papers/outline.tex

@@
 A \textbf{Full Generalized Compiler} is a tool for programming language researchers, providing a \textit{dynamic framework} for easily modifying syntax of input and output languages.
-The grammar of a programming language can be modified without recompiling the software.
-This is demonstrated by how easily a new programming language can be invented with Progtran.
-However, Progtran also uses this concept (dynamic syntax changes) to re-implement existing source-to-source compilation tools, such as \textbf{Cython} or \textbf{2to3}.
+A new programming language can even be fully implemented without recompiling the software.
+However, Progtran also uses this concept (user defined dynamic grammars) to re-implement existing source-to-source compilation tools, such as \textbf{Cython} or \textbf{2to3}.
 

### 2017-02-02 examples/class/main.py
Fixes bug with identifier overload lexing

@@ -1,2 +1,4 @@
 
 class Object():
+    def __init__(self):
+        print('Created Object')

### 2017-02-02 src/lex/lexmap.cpp

@@ -68,21 +68,21 @@ namespace lex
      */
     tuple<Token, vector<string>> LexMap::identify(vector<string> terms) const
     {
-        string text;
-        for (auto term : terms)
-        {
-            text += term;
-        }
         // Return result of first lexer to match against remaining terms
         for (auto lexer : language_lexers)
         {
             auto result = lexer.match(terms);
             if(result.result)
             {
+                string text;
+                for (auto term : result.consumed)
+                {
+                    text += term;
+                }
                 //print("vector<string> identified as " + lexer.name);
-                string type = lexer.type == "*text*" ? text
-                                                     : lexer.type;
-                return make_tuple(Token(result.consumed, lexer.name, type), result.remaining);
+                string name = lexer.name == "*text*" ? text
+                                                     : lexer.name;
+                return make_tuple(Token(result.consumed, name, lexer.type), result.remaining);
             }
         }
 

### 2017-02-02 examples/class/main.py
Temporarily fixes class example

@@ -2,3 +2,4 @@
 class Object():
     def __init__(self):
         print('Created Object')
+

### 2017-02-04 examples/value/main.py
Improves anyOf function

@@ -2,7 +2,3 @@
 
 if __name__ == "__main__":
     a = self.outgoing[word]
-    self.outgoing[word] += "b"
-    key = heaviest[r.randint(0, len(heaviest)-1)]
-    self.wordlist[w].incrementCount()
-    s = sorted(self.wordlist.keys(), key=lambda word: self.wordlist[word].count)

### 2017-02-04 src/match/match.hpp

@@ -135,10 +135,10 @@ namespace match
             for (auto matcher : matchers)
             {
                 auto match_result = matcher(terms);
-                if(match_result.result)
+                if ((match_result.result and match_result.consumed.size() > result.consumed.size()) 
+                     or not result.result)
                 {
                     result = match_result;
-                    break;
                 }
             }
             return result;

### 2017-02-05 papers/paper.tex
Adds benchmark results to paper

\documentclass{article}

\usepackage{indentfirst}
\usepackage{setspace}
\doublespacing

% Packages for showing source code
\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
language=C,
aboveskip=1mm,
belowskip=1mm,
showstringspaces=false,
columns=flexible,
basicstyle={\small\ttfamily},
numbers=none,
numberstyle=\tiny\color{gray},
keywordstyle=\color{blue},
commentstyle=\color{dkgreen},
stringstyle=\color{mauve},
breaklines=true,
breakatwhitespace=true,
tabsize=3
}

\title{Fully Generalized Compilation}
\date{01-26-2017}
\author{Lucas Saldyt}

\begin{document}

\maketitle
\pagenumbering{gobble}
\newpage
\pagenumbering{arabic}

\section{Abstract}

Assuming that two languages are \textit{isomorphic}, one syntax can be converted to another if given an adequate description of each syntax's grammar.
At an abstract level, this conversion is entirely practical. 
Progtran is an investigation into the feasibility of a \textbf{Fully Generalized Compiler}, a multi-language source-to-source compiler. 
Given source code in one language, a description of its grammar \textbf{A} , and a description of an output language's grammar \textbf{B}, can \textbf{A} be converted to \textbf{B} such that the output in \textbf{B} is indistinguishable from a program originally written in \textbf{B}?

\section{Introduction}

A \textbf{Full Generalized Compiler} is a tool for programming language researchers, providing a \textit{dynamic framework} for easily modifying syntax of input and output languages. 
A new programming language can even be fully implemented without recompiling the software. 
Progtran also uses this concept (user defined dynamic grammars) to re-implement existing source-to-source compilation tools, such as \textbf{Cython} or \textbf{2to3}.

\section{Methods}
\subsection{Grammars}
\subsection{Constructors}
\subsection{AST Transformations}

\section{Results}
\subsection{Quicksort Cython Comparison}
This is not meant to be a robust benchmark. Instead, it aims to show that Cython and Transpilation yield similar results.

Output for 1000 sorting iterations:
\begin{center}
    \begin{verbatim}
        Transpile speedup:
        13.335545461765733
        Cython speedup:
        13.9866371311344
        Transpile : Cython comparison (1> indicates transpile is faster than cython)
        0.9534490197132998
    \end{verbatim}
\end{center}

\newpage
\subsection{Original Python Code}

\lstset{language=Python}
\begin{lstlisting}
def sort(array):
    less    = []
    equal   = []
    greater = []

    if len(array) <= 1:
        return array
    else:
        pivot = array[0]
        for x in array:
            if x < pivot:
                less.append(x)
            if x == pivot:
                equal.append(x)
            if x > pivot:
                greater.append(x)
        return sort(less) + equal + sort(greater)

def main():
    l = sort([3, 2, 12, 9, 4, 68, 17, 1, 2, 3, 4, 5, 6, 12, 9  , 8, 7, 6,5, 4, 743])

if __name__ == "__main__":
    main()
\end{lstlisting}

\lstset{language=C}

\newpage
\subsection{Generated C++ Code (Glossa)}

\begin{lstlisting}
#include "../std/std.hpp"
template <typename T_array>
auto sort (T_array array)
{
    auto less = std::vector<Object>({});
    auto equal = std::vector<Object>({});
    auto greater = std::vector<Object>({});
    if (len(array) <= 1)
    {
        return array;
    }
    else
    {
        auto pivot = array[0];
        for (auto x : array)
        {
            if (x < pivot)
            {
                less.push_back(x);
            }
            if (x == pivot)
            {
                equal.push_back(x);
            }
            if (x > pivot)
            {
                greater.push_back(x);
            }
        };
        return sort(less) + equal + sort(greater);
    };
}
\end{lstlisting}

\newpage
\subsection{Generated C Code (Cython)}

Generated code for Cython is much more complex, as it integrates with the Python FFI

For example, this snippet declares an empty array

\begin{lstlisting}
  /* "main.py":6
 *     Sorts an array of comparable values
 *     """
 *     less    = []             # <<<<<<<<<<<<<<
 *     equal   = []
 *     greater = []
 */
  __pyx_t_1 = PyList_New(0); if (unlikely(!__pyx_t_1)) {__pyx_filename = __pyx_f[0]; __pyx_lineno = 6; __pyx_clineno = __LINE__; goto __pyx_L1_error;}
  __Pyx_GOTREF(__pyx_t_1);
  __pyx_v_less = ((PyObject*)__pyx_t_1);
  __pyx_t_1 = 0;
\end{lstlisting}

\end{document}

### 2017-02-05 papers/paper.tex
Adds basic compiler diagram

@@
 
+% Package for flowcharts/diagrams
+
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric, arrows}
+
+\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
+\tikzstyle{io} = [rectangle, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
+\tikzstyle{process} = [diamond, minimum width=2cm, minimum height=0cm, text centered, draw=black, fill=orange!30]
+\tikzstyle{arrow} = [thick,->,>=stealth]
+
+% ==================================================
+% Begin Paper
+% ==================================================
+
 \title{Fully Generalized Compilation}
@@
 \section{Methods}
+
 \subsection{Grammars}
@@
 
+\newpage
+
+\begin{tikzpicture}[node distance=2.5cm]
+
+    \node (sourcea) [startstop]                 {Source Code A};
+    \node (lexer)   [process, below of=sourcea] {Lexical Analyzer};
+    \node (tokens)  [io, below of=lexer]        {Symbolic Tokens};
+    \node (parser)  [process, below of=tokens]  {Parser};
+    \node (asta)    [io, below of=parser]       {AST};
+    \node (trans)   [process, below of=asta]    {Transformer};
+    \node (astb)    [io, below of=trans]        {Intermediate AST};
+    \node (gen)     [process, below of=astb]    {Generator};
+    \node (stop)    [startstop, below of=gen]   {Source Code B};
+
+    \draw [arrow] (sourcea) -- (lexer);
+    \draw [arrow] (lexer) -- (tokens);
+    \draw [arrow] (tokens) -- (parser);
+    \draw [arrow] (parser) -- (asta);
+    \draw [arrow] (asta) -- (trans);
+    \draw [arrow] (trans) -- (astb);
+    \draw [arrow] (astb) -- (gen);
+    \draw [arrow] (gen) -- (stop);
+
+\end{tikzpicture}
+
 \section{Results}
 \subsection{Quicksort Cython Comparison}
+
 This is not meant to be a robust benchmark. Instead, it aims to show that Cython and Transpilation yield similar results.

### 2017-02-06 papers/paper.tex
Improves paper outline

@@
 
-% Packages for showing source code
+% ================================================================================= 
+% Package for showing source code
+% =================================================================================
+
 \usepackage{listings}
@@
 language=C,
-aboveskip=1mm,
-belowskip=1mm,
+aboveskip=.5mm,
+belowskip=.5mm,
 showstringspaces=false,
 columns=flexible,
-basicstyle={\small\ttfamily},
+basicstyle={\scriptsize\ttfamily},
 numbers=none,
@@
 stringstyle=\color{mauve},
-breaklines=true,
+breaklines=false,
 breakatwhitespace=true,
@@
 
+% ================================================================================= 
 % Package for flowcharts/diagrams
+% =================================================================================
 
@@
 % ==================================================
-% Begin Paper
+% Paper
 % ==================================================
@@
 
+% ==================================================
 \section{Abstract}
+% ==================================================
 
-Assuming that two languages are \textit{isomorphic}, one syntax can be converted to another if given an adequate description of each syntax's grammar.
-At an abstract level, this conversion is entirely practical. 
+Assuming that two languages are \textit{isomorphic}, one language can be converted to another if given an adequate description of each language's grammar.
+At an abstract level, this conversion is entirely practical. However, in practice,  
 Progtran is an investigation into the feasibility of a \textbf{Fully Generalized Compiler}, a multi-language source-to-source compiler. 
@@
 
+% ==================================================
 \section{Introduction}
+% ==================================================
 
@@
 
+% ==================================================
 \section{Methods}
+% ==================================================
+
+\subsection{Traditional Compilation}
+Brief description of how compilers work
+
+\subsection{Abstracting Language Definitions}
+Description of grammar, transformation, and constructor files
 
 \subsection{Grammars}
+Influence of formal grammars
+
+Description of grammar file implementations
+
+\subsection{AST Transformations}
+
+Reasoning for and description of AST-transformations
+
 \subsection{Constructors}
-\subsection{AST Transformations}
+
+Description of Constructor implementation
+
+\subsection{Compilation in Glossa}
+Given all of the above details, how does compilation in Glossa compare to the traditional compilation process?
+
+(Grammar/Transform/Construction rules are read at run-time)
 
@@
 
+% ==================================================
+\section{Applications}
+% ==================================================
+
+\subsection{Re-implementation of Cython and 2to3}
+Description of implementing these two pieces of software with glossa
+
+\subsection{Cython}
+\subsection{2to3}
+
+\subsection{Comparisons and Benchmarks}
+
+\subsection{Simple code porting}
+Reference work on 2to3, talk about FORTRAN and similar conversions
+
+\subsection{Language Creation}
+Description of implementing new programming languages using glossa
+
+\subsection{Language Design and Modification}
+\subsection{Glossa as a pre-processor}
+
+% ==================================================
 \section{Results}
+% ==================================================
+
+\subsection{Results Overview}
+
+2to3 comparison
+
+Cython comparison
+
+GHC comparison
+
 \subsection{Quicksort Cython Comparison}
@@
         13.9866371311344
-        Transpile : Cython comparison (1> indicates transpile is faster than cython)
-        0.9534490197132998
+        Transpile : Cython comparison 
+        0.9534
     \end{verbatim}
@@
 
+\newpage
+
+% ==================================================
+\section{Conclusion}
+% ==================================================
+
 \end{document}

### 2017-02-06 demo.py
Improves python3 -> cpp class dynamics

@@ -126,6 +126,8 @@ def transpile(demoname, demos, verbosity, runcomp=False, runlang=True):
         languageargs = l[1:]
         build(directory, languageargs, verbosity)
         if languageargs[0] in ['python2', 'python3', 'auta']:
+            if os.path.exists('output/__pylib__'):
+                shutil.rmtree('output/__pylib__')
             shutil.copytree('std/__pylib__/', 'output/__pylib__')
 	# Save demo output before trying to run anything else
         outputdir = 'examples/output/' + demoname + '_output'

### 2017-02-06 examples/class/main.py

@@ -1,5 +1,8 @@
 
-class Object():
+class A():
     def __init__(self):
         print('Created Object')
+        self.x = 2
 
+if __name__ == '__main__':
+    A()

### 2017-02-06 std/cpp/object.hpp
Creates example of python-like members

@@ -105,6 +105,7 @@ public:
         : p( other.p->clone() ) {}
     Object( Object && other ) noexcept 
         : p( std::move(other.p) ) {}
+    Object();
     void swap( Object & other ) noexcept 
         { p.swap(other.p); }
     Object & operator=( Object other ) 

### 2017-02-07 examples/class/main.py
Adds python3 class functionality

@@ -4,5 +4,9 @@ class A():
         print('Created Object')
         self.x = 2
 
+    def foo(self, x):
+        print(x*x)
+
 if __name__ == '__main__':
-    A()
+    a = A()
+    a.foo(2)

### 2017-02-07 src/compiler.cpp
Removes current AST-transform feature

@@ -105,21 +105,6 @@ namespace compiler
     }
 
     /**
-     * High level function for loading a transformer map for a language
-     * @param language Language for transformer to be loaded for
-     * @return TransformerMap which can manipulate AST for the given language
-     */
-    TransformerMap loadTransformer (string language)
-    {
-        print("Loading transformers for " + language);
-        auto transformer_files = readFile("languages/" + language + "/transformers/core");
-        auto transformer = TransformerMap(transformer_files, "languages/" + language + "/transformers/");
-        print("Done");
-        return transformer;
-
-    }
-
-    /**
      * High level function for transpilation
      * Converts source files of one language to source files of another, copying them into a new directory
      * @param filenames   List of files to transpile
@@ -133,7 +118,6 @@ namespace compiler
     {
         auto grammar     = loadGrammar(input_lang);
         auto generator   = loadGenerator(output_lang);
-        auto transformer = loadTransformer(input_lang);
 
         auto symbol_table = readSymbolTable("languages/symboltables/" + input_lang + output_lang);
 
@@ -141,7 +125,7 @@ namespace compiler
 
         for (auto& file : filenames)
         {
-            compile(file, grammar, generator, transformer, symbol_table, input_dir, output_dir, logger);
+            compile(file, grammar, generator, symbol_table, input_dir, output_dir, logger);
         }
     }
 
@@ -155,7 +139,7 @@ namespace compiler
      * @param output_directory String name of output directory
      * @param logger           OutputManager class for managing verbose output. Use instead of print() calls
      */
-    void compile(string filename, Grammar& grammar, Generator& generator, TransformerMap& transformer,
+    void compile(string filename, Grammar& grammar, Generator& generator,
                  unordered_map<string, string>& symbol_table, string input_directory, 
                  string output_directory, OutputManager logger)
     {
@@ -175,8 +159,6 @@ namespace compiler
         auto identified_groups = grammar.identifyGroups(joined_tokens, logger);
         logger.log("Identified groups AST:");
         showAST(identified_groups, logger);
-        transformer(identified_groups);
-        logger.log("Transformed groups AST:");
         showAST(identified_groups, logger);
         logger.log("Compiling identified groups");
         auto files = compileGroups(identified_groups, filename, generator, logger);

### 2017-02-07 src/transform/transformer.cpp

@@ -3,139 +3,4 @@
 
 namespace transform 
 {
-
-/**
- * Constructs a transformer 
- * @param filenames Construction files
- * @param directory Directory that construction files reside in
- */
-TransformerMap::TransformerMap(vector<string> filenames, string directory)
-{
-    for (auto filename : filenames)
-    {
-        print("Reading transformer " + directory + filename);
-        readTransformerFile(directory + filename);
-    }
-}
-
-void TransformerMap::operator()(IdentifiedGroups& identified_groups)
-{
-    print("Performing transformation of identified groups");
-    for (auto& group : identified_groups)
-    {
-        auto& tag    = get<0>(group);
-        auto& matrix = get<1>(group);
-        transform(tag, matrix);
-    }
-}
-
-void TransformerMap::readTransformerFile(string filename)
-{
-    auto content = readFile(filename);
-    
-    // Seperate constructor into header and source constructors
-    assert(contains(content, "name"s));
-    auto name_i = std::find(content.begin(), content.end(), "name");
-    assert(name_i + 1 != content.end());
-    auto name         = *(name_i + 1);
-    auto declarations = vector<string>(content.begin(), name_i);
-    auto body         = vector<string>(name_i + 2, content.end());
-
-    transformers.push_back(make_tuple(name, readTransformer(body), generateSymbolStorageGenerator(declarations)));
-}
-
-Transformer TransformerMap::readTransformer(vector<string> content)
-{
-    string name = "symbol_list";
-    if (not content.empty())
-    {
-        name = content[0];
-        content = slice(content, 1);
-    }
-    return [content, name](SymbolMatrix matrix, SymbolStorage& symbol_storage){
-        SymbolMatrix new_matrix;
-        SymbolMatrix temp_matrix;
-        string tag = "undefined";
-        for (auto line : content)
-        {
-            vector<shared_ptr<Symbol>> temp_row;
-            auto terms = lex::seperate(line, {make_tuple(" ", false)});
-            assert(terms.size() > 0);
-            if (terms[0] == "new")
-            {
-                if (not temp_matrix.empty())
-                {
-                    new_matrix.push_back( vector<shared_ptr<Symbol>>({ make_shared<Symbol>(
-                                    MultiSymbol(tag, temp_matrix))   }) );
-                    temp_matrix.clear();
-                }
-                assert(terms.size() == 2);
-                tag = terms[1];
-            }
-            else
-            {
-                for (auto term : terms)
-                {
[…]

### 2017-02-07 src/gen/generator.cpp
Abstracts ec_creator from generateBranch function

@@ -102,7 +102,8 @@ vector<tuple<string, Constructor<string>>> Generator::readConstructor(string fil
             auto body = vector<string>(last_it + 1, it);
             //print("Created body");
             auto constructor = Constructor<string>(symbol_storage_generator, 
-                                                   generateBranch(body, symbol_storage_generator),
+                                                   generateBranch(body, symbol_storage_generator, 
+                                                       [this](string s){return this->generateElementConstructor(s);}),
                                                    definitions);
             constructors.push_back(make_tuple(type, constructor));
             last_it = it;
@@ -111,7 +112,11 @@ vector<tuple<string, Constructor<string>>> Generator::readConstructor(string fil
         //print("Done");
     }
     auto body = vector<string>(last_it + 1, content.end());
-    auto constructor = Constructor<string>(symbol_storage_generator, generateBranch(body, symbol_storage_generator), definitions);
+    auto constructor = Constructor<string>(symbol_storage_generator, 
+                                           generateBranch(body, 
+                                                          symbol_storage_generator, 
+                                                          [this](string s){return this->generateElementConstructor(s);}), 
+                                           definitions);
     constructors.push_back(make_tuple(type, constructor));
 
     return constructors;
@@ -329,10 +334,12 @@ string Generator::formatSymbol (string s, unordered_set<string>& names, SymbolSt
  * Create a branch from lines in a constructor file
  * @param content Lines of constructor file
  * @param symbol_storage_generator Function for creating symbol storage
+ * @param ec_creator function defining how to build an element constructor
  * @return Branch<string> which will follow user-defined logic to build a syntax element
  */
 Branch<string> Generator::generateBranch(vector<string> content, 
-                         SymbolStorageGenerator symbol_storage_generator)
+                         SymbolStorageGenerator symbol_storage_generator,
+                         ElementConstructorCreator<string> ec_creator)
 {
     vector<ElementConstructor<string>> line_constructors;
     vector<Branch<string>>             nested_branches;
@@ -347,7 +354,7 @@ Branch<string> Generator::generateBranch(vector<string> content,
     const auto addNestedBranch = [&](auto start, auto end, auto conditionline, bool inverse)
     {
         vector<string> body(start, end);
-        auto nested_branch                = generateBranch(body, symbol_storage_generator);
+        auto nested_branch                = generateBranch(body, symbol_storage_generator, ec_creator);
[…]

### 2017-02-07 src/gen/generator.hpp

@@ -29,7 +29,9 @@ private:
     void readStructureFile(string filename);
 
     Constructor<string>        generateConstructor(vector<string> content, SymbolStorageGenerator symbol_storage_generator);
-    Branch<string>             generateBranch(vector<string> content, SymbolStorageGenerator symbol_storage_generator);
+    Branch<string>             generateBranch(vector<string> content, 
+                                              SymbolStorageGenerator symbol_storage_generator, 
+                                              ElementConstructorCreator<string> ec_creator);
     ElementConstructor<string> generateElementConstructor(string line);
     ElementConstructor<string> generateSpecialElementConstructor(string line);
 };

### 2017-02-08 src/gen/generator.cpp
Abstracts generateBranch and generateConstructor

@@ -66,63 +66,10 @@ void Generator::readStructureFile(string filename)
  */
 vector<tuple<string, Constructor<string>>> Generator::readConstructor(string filename)
 {
-    auto content = readFile(filename);
-    
-    // Seperate constructor into header and source constructors
-    assert(contains(content, "defines"s));
-    auto defines_i = std::find(content.begin(), content.end(), "defines");
-    auto declarations = vector<string>(content.begin(), defines_i);
-
-    auto symbol_storage_generator = generateSymbolStorageGenerator(declarations);
-    vector<string> definitions;
-
-    string type = "definitions";
-    string tag;
-    bool first = true;
-    auto last_it = content.begin();
-    auto it = content.begin();
-
-    // Iterate over file types for each constructor file
-    vector<tuple<string, Constructor<string>>> constructors;
-    for (auto file_constructor : file_constructors)
-    {
-        tag = get<0>(file_constructor);
-        //print(tag);
-        assert(contains(content, tag));
-        it = std::find(content.begin(), content.end(), tag);
-
-        if (first)
-        {
-            definitions  = vector<string>(defines_i + 1, it);
-            last_it = it;
-            first = false;
-        }
-        else
-        {
-            auto body = vector<string>(last_it + 1, it);
-            //print("Created body");
-            auto constructor = Constructor<string>(symbol_storage_generator, 
-                                                   generateBranch(body, symbol_storage_generator, 
-                                                       [this](string s){return this->generateElementConstructor(s);}),
-                                                   definitions);
-            constructors.push_back(make_tuple(type, constructor));
-            last_it = it;
-        }
-        type = tag;
-        //print("Done");
-    }
-    auto body = vector<string>(last_it + 1, content.end());
-    auto constructor = Constructor<string>(symbol_storage_generator, 
-                                           generateBranch(body, 
-                                                          symbol_storage_generator, 
-                                                          [this](string s){return this->generateElementConstructor(s);}), 
-                                           definitions);
-    constructors.push_back(make_tuple(type, constructor));
-
-    return constructors;
+    auto content    = readFile(filename);
+    auto ec_creator = [this](string s){ return this->generateElementConstructor(s);}; 
+    return generateConstructor(content, file_constructors, ec_creator);
 }
-
-
 
 
 /**
@@ -328,104 +275,6 @@ string Generator::formatSymbol (string s, unordered_set<string>& names, SymbolSt
         }
     }
[…]

### 2017-02-08 src/gen/generator.hpp

@@ -28,10 +28,6 @@ private:
     vector<tuple<string, Constructor<string>>> readConstructor(string filename);
     void readStructureFile(string filename);
 
-    Constructor<string>        generateConstructor(vector<string> content, SymbolStorageGenerator symbol_storage_generator);
-    Branch<string>             generateBranch(vector<string> content, 
-                                              SymbolStorageGenerator symbol_storage_generator, 
-                                              ElementConstructorCreator<string> ec_creator);
     ElementConstructor<string> generateElementConstructor(string line);
     ElementConstructor<string> generateSpecialElementConstructor(string line);
 };

### 2017-02-08 src/gen/read.cpp

@@ -144,5 +144,159 @@ ConditionEvaluator generateConditionEvaluator(vector<string> terms)
     }
 }
 
+/**
+ * Create a branch from lines in a constructor file
+ * @param content Lines of constructor file
+ * @param symbol_storage_generator Function for creating symbol storage
+ * @param ec_creator function defining how to build an element constructor
+ * @return Branch<string> which will follow user-defined logic to build a syntax element
+ */
+Branch<string> generateBranch(vector<string> content, 
+                         SymbolStorageGenerator symbol_storage_generator,
+                         ElementConstructorCreator<string> ec_creator)
+{
+    vector<ElementConstructor<string>> line_constructors;
+    vector<Branch<string>>             nested_branches;
+
+    auto if_body_start   = content.begin();
+    auto else_body_start = content.begin(); // For collecting and processing contents of an if statement body
+    auto if_body_end     = content.begin();
+    auto else_body_end   = content.begin();
+
+    bool has_else = false;
+
+    const auto addNestedBranch = [&](auto start, auto end, auto conditionline, bool inverse)
+    {
+        vector<string> body(start, end);
+        auto nested_branch                = generateBranch(body, symbol_storage_generator, ec_creator);
+        auto original_condition_terms     = lex::seperate(*conditionline, {make_tuple(" ", false)});
+        if (inverse)
+        {
+            nested_branch.condition_evaluator = inverseBranch(generateConditionEvaluator(slice(original_condition_terms, 1)));
+        }
+        else
+        {
+            nested_branch.condition_evaluator = generateConditionEvaluator(slice(original_condition_terms, 1));
+        }
+        nested_branches.push_back(nested_branch);
+    };
+
+
+    int nest_count = 0;
+
+    auto it = content.begin();
+    while (it != content.end())
+    {
+        auto terms = lex::seperate(*it, {make_tuple(" ", false)});
+        if (not terms.empty())
+        {
+            auto keyword = terms[0];
+            if (keyword == "branch")
+            {
+                if (nest_count == 0)
+                {
+                    if_body_start = it;
+                    nested_branches.push_back(Branch<string>(defaultBranch, line_constructors, {}));
+                    line_constructors.clear();
+                }
+                nest_count++;
+            }
+            else if (keyword == "elsebranch")
+            {
+                if (nest_count == 1)
+                {
+                    if_body_end     = it;
+                    else_body_start = it;
+                    has_else = true;
+                }
+            }
+            else if (keyword == "end")
+            {
+                if (nest_count == 1)
+                {
[…]

### 2017-02-08 src/gen/read.hpp

@@ -6,5 +6,12 @@ namespace gen
 {
     SymbolStorageGenerator generateSymbolStorageGenerator(vector<string> content);
     ConditionEvaluator     generateConditionEvaluator(vector<string> terms);
+    Branch<string>         generateBranch(vector<string> content, 
+                                          SymbolStorageGenerator symbol_storage_generator, 
+                                          ElementConstructorCreator<string> ec_creator);
+
+    vector<tuple<string, Constructor<string>>> generateConstructor(vector<string> content, 
+            vector<tuple<string, FileConstructor>> file_constructors,
+            ElementConstructorCreator<string> ec_creator);
 
 }

### 2017-02-08 src/gen/generator.cpp
Templatizes generateConstructor and generateBranch

@@ -68,7 +68,7 @@ vector<tuple<string, Constructor<string>>> Generator::readConstructor(string fil
 {
     auto content    = readFile(filename);
     auto ec_creator = [this](string s){ return this->generateElementConstructor(s);}; 
-    return generateConstructor(content, file_constructors, ec_creator);
+    return generateConstructor<string>(content, file_constructors, ec_creator);
 }
 
 

### 2017-02-08 src/gen/read.cpp

@@ -144,159 +144,6 @@ ConditionEvaluator generateConditionEvaluator(vector<string> terms)
     }
 }
 
-/**
- * Create a branch from lines in a constructor file
- * @param content Lines of constructor file
- * @param symbol_storage_generator Function for creating symbol storage
- * @param ec_creator function defining how to build an element constructor
- * @return Branch<string> which will follow user-defined logic to build a syntax element
- */
-Branch<string> generateBranch(vector<string> content, 
-                         SymbolStorageGenerator symbol_storage_generator,
-                         ElementConstructorCreator<string> ec_creator)
-{
-    vector<ElementConstructor<string>> line_constructors;
-    vector<Branch<string>>             nested_branches;
 
-    auto if_body_start   = content.begin();
-    auto else_body_start = content.begin(); // For collecting and processing contents of an if statement body
-    auto if_body_end     = content.begin();
-    auto else_body_end   = content.begin();
-
-    bool has_else = false;
-
-    const auto addNestedBranch = [&](auto start, auto end, auto conditionline, bool inverse)
-    {
-        vector<string> body(start, end);
-        auto nested_branch                = generateBranch(body, symbol_storage_generator, ec_creator);
-        auto original_condition_terms     = lex::seperate(*conditionline, {make_tuple(" ", false)});
-        if (inverse)
-        {
-            nested_branch.condition_evaluator = inverseBranch(generateConditionEvaluator(slice(original_condition_terms, 1)));
-        }
-        else
-        {
-            nested_branch.condition_evaluator = generateConditionEvaluator(slice(original_condition_terms, 1));
-        }
-        nested_branches.push_back(nested_branch);
-    };
-
-
-    int nest_count = 0;
-
-    auto it = content.begin();
-    while (it != content.end())
-    {
-        auto terms = lex::seperate(*it, {make_tuple(" ", false)});
-        if (not terms.empty())
-        {
-            auto keyword = terms[0];
-            if (keyword == "branch")
-            {
-                if (nest_count == 0)
-                {
-                    if_body_start = it;
-                    nested_branches.push_back(Branch<string>(defaultBranch, line_constructors, {}));
-                    line_constructors.clear();
-                }
-                nest_count++;
-            }
-            else if (keyword == "elsebranch")
-            {
-                if (nest_count == 1)
-                {
-                    if_body_end     = it;
-                    else_body_start = it;
-                    has_else = true;
-                }
-            }
-            else if (keyword == "end")
-            {
-                if (nest_count == 1)
-                {
[…]

### 2017-02-08 src/gen/read.hpp

@@ -6,12 +6,163 @@ namespace gen
 {
     SymbolStorageGenerator generateSymbolStorageGenerator(vector<string> content);
     ConditionEvaluator     generateConditionEvaluator(vector<string> terms);
-    Branch<string>         generateBranch(vector<string> content, 
-                                          SymbolStorageGenerator symbol_storage_generator, 
-                                          ElementConstructorCreator<string> ec_creator);
 
-    vector<tuple<string, Constructor<string>>> generateConstructor(vector<string> content, 
+    /**
+     * Create a branch from lines in a constructor file
+     * @param content Lines of constructor file
+     * @param symbol_storage_generator Function for creating symbol storage
+     * @param ec_creator function defining how to build an element constructor
+     * @return Branch<string> which will follow user-defined logic to build a syntax element
+     */
+    template <typename T>
+    Branch<T> generateBranch(vector<string> content, 
+                             SymbolStorageGenerator symbol_storage_generator,
+                             ElementConstructorCreator<T> ec_creator)
+    {
+        vector<ElementConstructor<T>> line_constructors;
+        vector<Branch<T>>             nested_branches;
+
+        auto if_body_start   = content.begin();
+        auto else_body_start = content.begin(); // For collecting and processing contents of an if statement body
+        auto if_body_end     = content.begin();
+        auto else_body_end   = content.begin();
+
+        bool has_else = false;
+
+        const auto addNestedBranch = [&](auto start, auto end, auto conditionline, bool inverse)
+        {
+            vector<string> body(start, end);
+            auto nested_branch                = generateBranch(body, symbol_storage_generator, ec_creator);
+            auto original_condition_terms     = lex::seperate(*conditionline, {make_tuple(" ", false)});
+            if (inverse)
+            {
+                nested_branch.condition_evaluator = inverseBranch(generateConditionEvaluator(slice(original_condition_terms, 1)));
+            }
+            else
+            {
+                nested_branch.condition_evaluator = generateConditionEvaluator(slice(original_condition_terms, 1));
+            }
+            nested_branches.push_back(nested_branch);
+        };
+
+
+        int nest_count = 0;
+
+        auto it = content.begin();
+        while (it != content.end())
+        {
+            auto terms = lex::seperate(*it, {make_tuple(" ", false)});
+            if (not terms.empty())
+            {
+                auto keyword = terms[0];
+                if (keyword == "branch")
+                {
+                    if (nest_count == 0)
+                    {
[…]

### 2017-02-08 demo.py
Improves benchmarking?

@@ -51,8 +51,8 @@ def time_run(language, directory, iterations, filename):
     os.chdir(directory + '_copy')
     try:
         for line in content[:-1]:
-            subprocess.check_output(line, shell=True) # Yes, this is unescaped.
-        t = benchmark(subprocess.check_output, iterations, content[-1], shell=True)
+            subprocess.call(line, shell=True) # Yes, this is unescaped.
+        t = benchmark(subprocess.call, iterations, content[-1], shell=True)
     finally:
         os.chdir(olddir)
         shutil.rmtree(directory + '_copy')
@@ -69,24 +69,24 @@ def run_language(directory, inputlang, outputlang):
         time_run(outputlang, 'output', 1, 'main')
 
 def compare(directory, inputlang, outputlang, iterations=1):
+    print('Input code:')
+    input_time = time_run(inputlang, directory, iterations, 'main')
+
     # Compile output c++ code (hardcoded for now, since output language is always c++)
+    print('Output code:')
     if outputlang == 'cpp':
         os.chdir('output')
         subprocess.run('g++ -std=c++17 *.cpp -O2 ../std/cpp/*.cpp', shell=True)
-        output_time = benchmark(subprocess.check_output, iterations, './a.out', shell=True)
+        output_time = benchmark(subprocess.call, iterations, './a.out', shell=True)
         os.chdir('..')
     else:
         output_time = time_run(outputlang, 'output', iterations, 'main')
-    print('Output code time:')
-    print(output_time)
 
+    '''
     # Timing of inputlang isn't hardcoded:
-    input_time = time_run(inputlang, directory, iterations, 'main')
-    print('Input code time:')
-    print(input_time)
-    print('Transpile speedup:')
-    transpile_speedup = input_time / output_time
-    print(transpile_speedup)
+    # print('Transpile speedup:')
+    # transpile_speedup = input_time / output_time
+    # print(transpile_speedup)
 
     if inputlang in ['python2', 'python3']:
         cythonversion = 'cython3' if inputlang == 'python3' else 'cython'
@@ -99,6 +99,7 @@ def compare(directory, inputlang, outputlang, iterations=1):
         
         print('Transpile : Cython comparison (1> indicates transpile is faster than cython)')
         print(transpile_speedup / cython_speedup)
+    '''
 
 def load_demos():
     # Build list of demonstrations
@@ -137,7 +138,7 @@ def transpile(demoname, demos, verbosity, runcomp=False, runlang=True):
[…]

### 2017-02-08 examples/python3/main.py

@@ -1,3 +1,4 @@
+from time import time
 
 def sort(array):
     """
@@ -21,7 +22,14 @@ def sort(array):
         return sort(less) + equal + sort(greater)
 
 def main():
-    l = sort([3, 2, 12, 9, 4, 68, 17, 1, 2, 3, 4, 5, 6, 12, 9  , 8, 7, 6,5, 4, 743])
+    iterations = 1000
+    r = range(iterations)
+    l = [] 
+    a = time()
+    for i in r:
+        l = sort(l)
+    b = time()
+    print(b - a)
 
 if __name__ == "__main__":
     main()

### 2017-02-08 std/cpp/chrono.hpp

@@ -1,0 +1,13 @@
+#include <chrono>
+#include <iostream>
+
+auto time()
+{
+    return std::chrono::high_resolution_clock::now();
+}
+
+std::ostream& operator <<(std::ostream& os, const std::chrono::duration<long int, std::ratio<1l, 1000000000l>>& t)
+{
+    os << t.count() << std::endl;
+    return os;
+}

### 2017-02-08 demo.py
Continues improving benchmarking

@@ -71,6 +71,7 @@ def run_language(directory, inputlang, outputlang):
 def compare(directory, inputlang, outputlang, iterations=1):
     print('Input code:')
     input_time = time_run(inputlang, directory, iterations, 'main')
+    print('%s seconds total' % input_time)
 
     # Compile output c++ code (hardcoded for now, since output language is always c++)
     print('Output code:')
@@ -81,25 +82,13 @@ def compare(directory, inputlang, outputlang, iterations=1):
         os.chdir('..')
     else:
         output_time = time_run(outputlang, 'output', iterations, 'main')
-
-    '''
-    # Timing of inputlang isn't hardcoded:
-    # print('Transpile speedup:')
-    # transpile_speedup = input_time / output_time
-    # print(transpile_speedup)
+    print('%s seconds total' % output_time)
 
     if inputlang in ['python2', 'python3']:
         cythonversion = 'cython3' if inputlang == 'python3' else 'cython'
+        print('Cython code:')
         cython_time = time_run(cythonversion, directory, iterations, 'main')
-        print('Cython time:')
-        print(cython_time)
-        print('Cython speedup:')
-        cython_speedup = cython_time / output_time
-        print(cython_speedup)
-        
-        print('Transpile : Cython comparison (1> indicates transpile is faster than cython)')
-        print(transpile_speedup / cython_speedup)
-    '''
+        print('%s seconds total' % cython_time)
 
 def load_demos():
     # Build list of demonstrations

### 2017-02-08 examples/benchmark/main.py

@@ -1,0 +1,15 @@
+from time import time
+
+def main():
+    iterations = 100
+    a = time()
+    b = time()
+    total = b - a 
+    for i in range(iterations):
+        a = time()
+        b = time()
+        total += (b - a)
+    print(total / (iterations + 1))
+
+if __name__ == "__main__":
+    main()

### 2017-02-08 examples/integrate/main.py

@@ -1,3 +1,5 @@
+from time import time
+
 def f(x):
     return x*x-x
 
@@ -9,5 +11,13 @@ def integrate_f(a, b, N):
     return s * dx
 
 if __name__ == "__main__":
-    print(integrate_f(1, 100, 200))
+    iterations = 1
+    N = 200
+    start = 1
+    r = list(range(iterations))
+    a = time()
+    for i in r:
+        integrate_f(start, i, N)
+    b = time()
+    print((b - a) / iterations)
 

### 2017-02-08 examples/python3/main.py

@@ -22,12 +22,7 @@ def sort(array):
         return sort(less) + equal + sort(greater)
 
 def main():
-    iterations = 1000
-    r = range(iterations)
-    l = [] 
     a = time()
-    for i in r:
-        l = sort(l)
     b = time()
     print(b - a)
 

### 2017-02-08 std/cpp/chrono.hpp

@@ -8,6 +8,6 @@ auto time()
 
 std::ostream& operator <<(std::ostream& os, const std::chrono::duration<long int, std::ratio<1l, 1000000000l>>& t)
 {
-    os << t.count() << std::endl;
+    os << std::chrono::duration_cast<std::chrono::duration<float>>(t).count();
     return os;
 }

### 2017-02-08 std/cpp/vectorhelpers.cpp

@@ -9,5 +9,5 @@ vector<Object> range(int b, int a, int step)
     {
         v.push_back(Object(i));
     }
-    return v;
+    return std::move(v);
 }

### 2017-02-09 examples/fortran/main.f90
Successfully adds fortan declarions/definitions

@@ -1,3 +1,5 @@
 PROGRAM hello 
+    REAL :: A
+    INTEGER :: B = 1
     WRITE(*,*) 'Hello World'
 END PROGRAM 

### 2017-02-09 src/gen/read.cpp

@@ -13,11 +13,9 @@ namespace gen
 SymbolStorageGenerator generateSymbolStorageGenerator(vector<string> content)
 {
     return [content](vector<vector<shared_ptr<Symbol>>>& symbol_groups){
-        //print("Building symbol storage");
         SymbolStorage storage;
         for (auto line : content)
         {
-            //print(line);
             auto terms = lex::seperate(line, {make_tuple(" ", false)});
             assert(terms.size() == 3 or 
                    terms.size() == 4);
@@ -63,6 +61,10 @@ SymbolStorageGenerator generateSymbolStorageGenerator(vector<string> content)
                 {
                     int index_a = std::stoi(terms[2]);
                     int index_b = std::stoi(terms[3]);
+                    if (symbol_groups.size() <= index_a)
+                    {
+                        print(line);
+                    }
                     assert(symbol_groups.size() > index_a);
                     if (symbol_groups[index_a].size() <= index_b)
                     {

### 2017-02-09 examples/fortran/main.f90
Adds lexing of floating point literals

@@ -1,5 +1,6 @@
 PROGRAM hello 
     REAL :: A
     INTEGER :: B = 1
+    REAL :: C = 2.3
     WRITE(*,*) 'Hello World'
 END PROGRAM 

### 2017-02-09 src/compiler.cpp

@@ -67,15 +67,16 @@ namespace compiler
         auto punctuators      = readFile(lex_dir + "punctuators");
 
         LexMapTermSets term_sets;
-        term_sets.push_back(make_tuple(grammar.keywords, "keyword"));         // Keywords are read in automatically from grammar file usage
-        term_sets.push_back(make_tuple(logicaloperators, "logicaloperator"));
-        term_sets.push_back(make_tuple(operators,        "operator"));
-        term_sets.push_back(make_tuple(punctuators,      "punctuator"));
+        term_sets.push_back(make_tuple(grammar.keywords, "keyword",         1));         // Keywords are read in automatically from grammar file usage
+        term_sets.push_back(make_tuple(logicaloperators, "logicaloperator", 3));
+        term_sets.push_back(make_tuple(operators,        "operator",        1));
+        term_sets.push_back(make_tuple(punctuators,      "punctuator",      3));
 
         vector<LexMapLexer> lexer_set = {
             LexMapLexer(just("    "s),     "tab",        "tab",        3),
             LexMapLexer(startswith("\t"s), "tab",        "tab",        3),
             LexMapLexer(digits,            "int",        "literal",    3),
+            LexMapLexer(doubles,           "double",     "literal",    1),
             LexMapLexer(identifiers,       "*text*",    "identifier", 3)};
 
         lexer_set.push_back(LexMapLexer(startswith(grammar.comment_delimiter), "comment", "comment", 3));

### 2017-02-09 src/match/base/locale.cpp

@@ -34,3 +34,11 @@ bool is_identifiers(const std::string &str)
     bool idents = all_of(str.begin(), str.end(), [](auto c){return isalpha(c) or isdigit(c) or c == '_';});
     return idents and not (is_digits(str));
 }
+
+bool is_double(const std::string &str)
+{
+    bool digits_and_dots = all_of(str.begin(), str.end(), [](auto c){
+            return isdigit(c) or c == '.';
+            });
+    return digits_and_dots and not is_digits(str); // Str cant be only digits 
+}

### 2017-02-09 src/match/match.hpp

@@ -236,4 +236,6 @@ namespace match
     const auto lowers = singleTemplate<string>(is_lowers);
     /// Parse a single string against valid identifier characters 
     const auto identifiers = singleTemplate<string>(is_identifiers);
+    /// Parse a double
+    const auto doubles = singleTemplate<string>(is_double);
 }

### 2017-02-09 src/syntax/symbols/export.hpp

@@ -10,6 +10,7 @@ namespace syntax
 {
     using Punctuator = StringLiteral;
     using Integer    = Literal<int>;
+    using Double     = Literal<double>;
     using Keyword    = StringLiteral;
     using Tab        = StringLiteral;
     using Newline    = StringLiteral;
@@ -28,6 +29,7 @@ namespace syntax
     };
     const auto keywordGenerator = [](string s){ return make_shared<Keyword>(Keyword(s)); };
     const auto intGenerator     = [](string s){ return make_shared<Integer>(Integer(stoi(s))); };
+    const auto doubleGenerator  = [](string s){ return make_shared<Double>(Double(stod(s))); };
     const auto puncGenerator    = [](string s){ return make_shared<Punctuator>(Punctuator(s));};
     const auto tabGenerator     = [](string s){ return make_shared<Tab>(Tab(s));};
     const auto commentGenerator = [](string s){ return make_shared<Comment>(Comment(string(s.begin() + 1, s.end()))); };
@@ -36,7 +38,15 @@ namespace syntax
     {
         shared_ptr<Symbol> value;
         try {
-            value = intGenerator(s);
+            auto found = s.find(".");
+              if (found != std::string::npos)
+              {
+                  value = doubleGenerator(s);
+              }
+              else
+              {
+                  value = intGenerator(s);
+              }
         }
         catch(std::exception)
         {

### 2017-02-09 tests/lex_tests.cpp

@@ -11,8 +11,8 @@ TEST_CASE("The lexer and language modules work")
     vector<string> operators = {"+", "-", "/", "*"};
 
     vector<LexMapTermSet> term_set;
-    term_set.push_back(make_tuple(keywords, "keyword"));
-    term_set.push_back(make_tuple(operators, "operator"));
+    term_set.push_back(make_tuple(keywords, "keyword", 1));
+    term_set.push_back(make_tuple(operators, "operator", 1));
 
     vector<LexMapLexer>  lexer_set;
     lexer_set.push_back(LexMapLexer(digits, "int", "type", 1));

### 2017-03-10 src/gen/generator.cpp
WIP

@@ -16,6 +16,12 @@ Generator::Generator(vector<string> filenames, string directory)
     {
         construction_map[filename] = readConstructor(directory + filename);
     }
+    ec_creator = [this](string s){ return this->generateElementConstructor(s);}; 
+    vector<string> default_body = {"branch contains val", "$val$", "end"};
+    default_constructor = Constructor<string>(
+                                generateBranch<string>(default_body, ec_creator),
+                                {}
+                                );
 }
 
 /**
@@ -93,16 +99,12 @@ vector<tuple<string, string, vector<string>>> Generator::operator()(unordered_se
     vector<tuple<string, Constructor<string>>> constructors;
     if (not contains(construction_map, symbol_type))
     {
-        ElementConstructorCreator<string> ec_creator = [this](string s){ return this->generateElementConstructor(s);}; 
-        vector<string> default_body = {"branch contains val", "$val$", "end"};
         for (auto fc : file_constructors)
         {
             auto filetype = get<0>(fc);
             constructors.push_back(make_tuple(filetype, 
-                        Constructor<string>(
-                            generateBranch<string>(default_body, ec_creator),
-                            {}
-                            )));
+                        default_constructor
+                            ));
         }
     }
     else

### 2017-03-10 src/gen/generator.hpp

@@ -36,6 +36,9 @@ private:
 
     ElementConstructor<string> generateElementConstructor(string line);
     ElementConstructor<string> generateSpecialElementConstructor(string line);
+
+    ElementConstructorCreator<string> ec_creator;
+    Constructor<string> default_constructor;
 };
 
 }

### 2017-03-11 papers/paper.tex
Minute changes to paper
WIP on paper rough draft

@@
 % ==================================================
-
+Glossa is an investigation into the feasibility of a multi-language source-to-source compiler with dynamic grammars. 
 Assuming that two languages are \textit{isomorphic}, one language can be converted to another if given an adequate description of each language's grammar.
-At an abstract level, this conversion is entirely practical. However, in practice,  
-Progtran is an investigation into the feasibility of a \textbf{Fully Generalized Compiler}, a multi-language source-to-source compiler. 
+At an abstract level, this conversion is entirely practical.
 Given source code in one language, a description of its grammar \textbf{A} , and a description of an output language's grammar \textbf{B}, can \textbf{A} be converted to \textbf{B} such that the output in \textbf{B} is indistinguishable from a program originally written in \textbf{B}?
+Once this is achieved, the grammar description for \textbf{A} can be modified, and the program will still output code in the \textbf{B} language that satisfies the above constraint.
 
@@
 
-A \textbf{Full Generalized Compiler} is a tool for programming language researchers, providing a \textit{dynamic framework} for easily modifying syntax of input and output languages. 
-A new programming language can even be fully implemented without recompiling the software. 
-Progtran also uses this concept (user defined dynamic grammars) to re-implement existing source-to-source compilation tools, such as \textbf{Cython} or \textbf{2to3}.
+A multi-language source to source compiler is potentially a tool for programming language researchers, providing a \textit{dynamic framework} for easily modifying syntax of input and output languages.
+Glossa also uses this concept to re-implement existing source-to-source compilation tools, such as \textbf{Cython} or \textbf{2to3}.
 
@@
 
-\subsection{Traditional Compilation}
-Brief description of how compilers work
+\subsection{Compilation}
+Traditionally, a compiler takes a single high-level programming language, and converts it into machine instructions.
+\begin{enumerate}
+\item Code is lexed (seperated into tokens and tagged as keywords, punctuators, literals, etc...)
+\item Tokens are parsed to build an abstract syntax tree (symbolic code representation)
+\item The AST is optimized (i.e. unreachable code is removed, some loops are unrolled)
+\item Machine instructions are generated.
+\end{enumerate}
+While some compilers and interpreters have dynamic ways to modify the syntax of a language, this functionality seems to be unneeded for most compilers.
+
+Glossa differs only slightly from the steps above. Lexing and parsing work as above, but the rules for lexing and parsing respectively are read in at run-time. 
+In the current state of the software, optimizations don't occur, but could easily be modeled as transformations to the abstract syntax tree.
+Instead of generating machine instructions, Glossa generates code in another programming language. 
+Instructions for doing this are also read in at run-time.
+Because of its dynamic nature, it is very simple to have Glossa support multiple programming languages both for input and output.
 
 \subsection{Abstracting Language Definitions}
-Description of grammar, transformation, and constructor files
+
+As outlined above, Glossa reads in parse/generate descriptions for programming languages at run-time.
+Additionally, Glossa reads in rules for transforming the abstract syntax tree.
+
+To parse an input language, Glossa needs a description of the languages grammar, which is provided through a \textit{grammar file}.
+Optional descriptions of AST transformations are provided through \textit{transformer files}.
+
+To generate an output language from an AST, Glossa needs a set of \textit{constructor files}.
 
@@
 Description of Constructor implementation
-
-\subsection{Compilation in Glossa}
-Given all of the above details, how does compilation in Glossa compare to the traditional compilation process?
-
-(Grammar/Transform/Construction rules are read at run-time)
 
@@
 \subsection{Quicksort Cython Comparison}
-
-This is not meant to be a robust benchmark. Instead, it aims to show that Cython and Transpilation yield similar results.
-
-Output for 1000 sorting iterations:
-\begin{center}
-    \begin{verbatim}
-        Transpile speedup:
-        13.335545461765733
-        Cython speedup:
-        13.9866371311344
-        Transpile : Cython comparison 
-        0.9534
-    \end{verbatim}
-\end{center}
 

### 2017-03-14 papers/paper.tex
Adds grammar file notes to paper

@@
 \item The AST is optimized (i.e. unreachable code is removed, some loops are unrolled)
-\item Machine instructions are generated.
+\item Machine instructions are generated from AST.
 \end{enumerate}
@@
 
-As outlined above, Glossa reads in parse/generate descriptions for programming languages at run-time.
-Additionally, Glossa reads in rules for transforming the abstract syntax tree.
-
 To parse an input language, Glossa needs a description of the languages grammar, which is provided through a \textit{grammar file}.
@@
 
-\subsection{Grammars}
-Influence of formal grammars
+\subsection{Grammar Files}
 
-Description of grammar file implementations
+Glossa's parse operation can be modeled as a function with the signature:
+
+parse :: Tokens -> AST
+
+Where the body of the parse function looks like:
+
+\lstset{language=Python}
+\begin{lstlisting}
+while not tokens.empty():
+    identify_remaining(tokens)
+\end{lstlisting}
+
+Glossa will attempt to identify remaining tokens with any of the high-level statement types provided.
+These statement types can use other grammar constructs as well
+
+A single grammar files defines a potential identification of tokens, producing a tagged dictionary of symbols if the tokens are identified successfully:
+
+The simplest non-trivial grammar file is likely the assignment statement:
+
+\verbatim
+assignment: `@lval identifier **` `@op '='` `@rval boolexpression | expression`
+\end{verbatim}
+
+In plain english this reads:
+"Parse an identifier, and save it to the symbol dictionary as `lval`, then parse an equals operator, and save it to `op`, lastly, parse a boolean expression or normal expression and save it to `rval`"
+
+In general, a grammar element is defined like the following:
+
+\verbatim
+name: `first_element` `second_element`
+\end{verbatim}
+
+Where first\_element and second\_element are parsers of the form:
+
+\verbatim
+an optional "@name" tag, which saves the result of the parser to the symbol dictionary under "name"
+Either:
+- A subtype parser (i.e `'='`),
+- A subtype-type parser (i.e. `identifier self`)
+- A type parser (i.e. `identifier **`)
+- A link to another grammar element (i.e. `value`)
+
+So, the following are all examples of valid parsers:
+`@val value`          // Link to value type, saved as "val"
+`identifier self`     // Identifier "self", discarded
+`@name identifier **` // Any identifier saved as "name"
+
+However, these parsers can be prefixed with the following keywords to change their meaning:
+
+!           : discard the parse result of this parser
+anyOf a b   : parse either a or b, keeping the result of the first successful parser. This has syntactic sugar of the form (a | b)
+*/many      : parse the parser several times until it fails
+many1       : parse the parser several times, requiring it to parse successfully at least once
+optional    : make a parser optional
+inOrder a b : run several parsers in order
+sep a b     : parse bs seperated by as (i.e. sep , value)
+
+Some examples of more sophisticated parsers
+
+`@statement import_from | main | ... ` 
+`@val identifier ** | string | literal ** | 'None' | 'True' | 'False'`
+`@val vector | functioncall | elementaccess | memberaccess | basevalue | parenexpr`
+`@args optional sep ',' expression`
+
+\end{verbatim}
 

### 2017-03-14 papers/paper.tex
Adds grammar file notes to paper

@@
 The simplest non-trivial grammar file is likely the assignment statement:
-
-\verbatim
+\begin{lstlisting}
     assignment: `@lval identifier **` `@op '='` `@rval boolexpression | expression`
-\end{verbatim}
+\end{lstlisting}
 
@@
 
-\verbatim
+\begin{lstlisting}
 name: `first_element` `second_element`
-\end{verbatim}
+\end{lstlisting}
 
@@
 
-\verbatim
+\begin{lstlisting}
 an optional "@name" tag, which saves the result of the parser to the symbol dictionary under "name"
@@
 `@args optional sep ',' expression`
-
-\end{verbatim}
+\end{lstlisting}
 

### 2017-03-16 papers/paper.tex
Finishes all sections besides results/conclusion

--- 2017-03-14 papers/paper.tex
@@
 Assuming that two languages are \textit{isomorphic}, one language can be converted to another if given an adequate description of each language's grammar.
-At an abstract level, this conversion is entirely practical.
 Given source code in one language, a description of its grammar \textbf{A} , and a description of an output language's grammar \textbf{B}, can \textbf{A} be converted to \textbf{B} such that the output in \textbf{B} is indistinguishable from a program originally written in \textbf{B}?
-Once this is achieved, the grammar description for \textbf{A} can be modified, and the program will still output code in the \textbf{B} language that satisfies the above constraint.
+Once this is achieved, the grammar description for \textbf{A} can be modified at will, changing \textbf{A}'s syntax, but keeping the \textbf{B} output the same.
 
@@
 
-A multi-language source to source compiler is potentially a tool for programming language researchers, providing a \textit{dynamic framework} for easily modifying syntax of input and output languages.
-Glossa also uses this concept to re-implement existing source-to-source compilation tools, such as \textbf{Cython} or \textbf{2to3}.
+Glossa provides a \textit{dynamic framework} for easily modifying syntax of input and output languages. 
+As programming paradigms shift, so does language syntax. Ultimately, modifiable syntax leads to better programming languages. 
+Since each programming language has its own compiler, there is some redundancy in each implementation.
+If programming languages could be compiled with a framework, this redundancy would go away, and programming language researchers would be able to focus on the language itself, as opposed to its compiler.
+
+Essentially, Glossa abstracts the parts of a compiler that don't depend on which language is being compiled, and reads in rules for each language, effectively seperating the language from how it is compiled.
 
@@
 \subsection{Compilation}
-Traditionally, a compiler takes a single high-level programming language, and converts it into machine instructions.
+Traditionally, a compiler takes a single high-level programming language, and converts it into machine instructions in the following steps:
 \begin{enumerate}
@@
 \end{enumerate}
-While some compilers and interpreters have dynamic ways to modify the syntax of a language, this functionality seems to be unneeded for most compilers.
 
@@
 In the current state of the software, optimizations don't occur, but could easily be modeled as transformations to the abstract syntax tree.
-Instead of generating machine instructions, Glossa generates code in another programming language. 
+Instead of generating machine instructions, Glossa generates code in another programming language. (See next page) 
 Instructions for doing this are also read in at run-time.
+While some compilers and interpreters have dynamic ways to modify the syntax of a language, this functionality seems to be unneeded for most compilers.
 Because of its dynamic nature, it is very simple to have Glossa support multiple programming languages both for input and output.
-
-\subsection{Abstracting Language Definitions}
-
-To parse an input language, Glossa needs a description of the languages grammar, which is provided through a \textit{grammar file}.
-Optional descriptions of AST transformations are provided through \textit{transformer files}.
-
-To generate an output language from an AST, Glossa needs a set of \textit{constructor files}.
-
-\subsection{Grammar Files}
-
-Glossa's parse operation can be modeled as a function with the signature:
-
-parse :: Tokens -> AST
-
-Where the body of the parse function looks like:
-
-\lstset{language=Python}
-\begin{lstlisting}
-while not tokens.empty():
-    identify_remaining(tokens)
-\end{lstlisting}
-
-Glossa will attempt to identify remaining tokens with any of the high-level statement types provided.
-These statement types can use other grammar constructs as well
-
-A single grammar files defines a potential identification of tokens, producing a tagged dictionary of symbols if the tokens are identified successfully:
-
-The simplest non-trivial grammar file is likely the assignment statement:
-
-\verbatim
-assignment: `@lval identifier **` `@op '='` `@rval boolexpression | expression`
-\end{verbatim}
-
-In plain english this reads:
-"Parse an identifier, and save it to the symbol dictionary as `lval`, then parse an equals operator, and save it to `op`, lastly, parse a boolean expression or normal expression and save it to `rval`"
-
-In general, a grammar element is defined like the following:
-
-\verbatim
-name: `first_element` `second_element`
-\end{verbatim}
-
-Where first\_element and second\_element are parsers of the form:
-
-\verbatim
-an optional "@name" tag, which saves the result of the parser to the symbol dictionary under "name"
-Either:
-- A subtype parser (i.e `'='`),
-- A subtype-type parser (i.e. `identifier self`)
-- A type parser (i.e. `identifier **`)
-- A link to another grammar element (i.e. `value`)
-
-So, the following are all examples of valid parsers:
-`@val value`          // Link to value type, saved as "val"
-`identifier self`     // Identifier "self", discarded
-`@name identifier **` // Any identifier saved as "name"
-
-However, these parsers can be prefixed with the following keywords to change their meaning:
-
-!           : discard the parse result of this parser
-anyOf a b   : parse either a or b, keeping the result of the first successful parser. This has syntactic sugar of the form (a | b)
-*/many      : parse the parser several times until it fails
-many1       : parse the parser several times, requiring it to parse successfully at least once
-optional    : make a parser optional
-inOrder a b : run several parsers in order
-sep a b     : parse bs seperated by as (i.e. sep , value)
-
-Some examples of more sophisticated parsers
-
-`@statement import_from | main | ... ` 
-`@val identifier ** | string | literal ** | 'None' | 'True' | 'False'`
-`@val vector | functioncall | elementaccess | memberaccess | basevalue | parenexpr`
-`@args optional sep ',' expression`
-
-\end{verbatim}
-
-\subsection{AST Transformations}
-
-Reasoning for and description of AST-transformations
-
-\subsection{Constructors}
-
-Description of Constructor implementation
 
@@
 
+\subsection{Abstracting Language Definitions}
+
+To parse an input language, Glossa needs a description of the languages grammar, which is provided through a \textit{grammar file}.
+Optional descriptions of AST transformations are provided through \textit{transformer files}.
+
+To generate an output language from an AST, Glossa needs a set of \textit{constructor files}.
+
+\subsection{Grammar Files}
+
+Glossa's parse operation can be modeled as a function with the signature:
+
+\begin{verbatim}
+parse :: Tokens -> AST
+\end{verbatim}
+
+Where the body of the parse function looks like:
+
+\lstset{language=Python}
+\begin{lstlisting}
+while not tokens.empty():
+    identify_remaining(tokens)
+\end{lstlisting}
+
+Glossa will attempt to identify remaining tokens with any of the high-level statement types provided.
+These statement types can use other grammar constructs as well
+
+A single grammar files defines a potential identification of tokens, producing a tagged dictionary of symbols if the tokens are identified successfully:
+
+The simplest non-trivial grammar file is likely the assignment statement:
+\begin{verbatim}
+assignment: `@lval identifier **` `@op '='` `@rval boolexpression | expression`
+\end{verbatim}
+
+In plain english this reads:
+\textit{"Parse an identifier, and save it to the symbol dictionary as `lval`, then parse an equals operator, and save it to `op`, lastly, parse a boolean expression or normal expression and save it to `rval`"}
+
+In general, a grammar element is defined like the following:
+
+\begin{verbatim}
+name: `first_element` `second_element`
+\end{verbatim}
+
+Where first\_element and second\_element are parsers of the form:
+
+\begin{verbatim}
+an optional "@name" tag, which saves the result of the parser to the symbol dictionary under "name"
+Either:
+- A subtype parser (i.e `'='`),
+- A subtype-type parser (i.e. `identifier self`)
+- A type parser (i.e. `identifier **`)
+- A link to another grammar element (i.e. `value`)
+
+So, the following are all examples of valid parsers:
+`@val value`          // Link to value type, saved as "val"
+`identifier self`     // Identifier "self", discarded
+`@name identifier **` // Any identifier saved as "name"
+
+However, these parsers can be prefixed with the following keywords to change their meaning:
+
+!           : discard the parse result of this parser
+anyOf a b   : parse either a or b, keeping the result of the first successful parser. 
+    (alternatively written a | b) 
+*/many      : parse the parser several times until it fails
+many1       : parse the parser several times, requiring it to parse successfully at least once
+optional    : make a parser optional
+inOrder a b : run several parsers in order
+sep a b     : parse bs seperated by as (i.e. sep , value)
+
+Some examples of more sophisticated parsers
+
+`@statement import_from | main | ... ` 
+`@val identifier ** | string | literal ** | 'None' | 'True' | 'False'`
+`@val vector | functioncall | elementaccess | memberaccess | basevalue | parenexpr`
+`@args optional sep ',' expression`
+\end{verbatim}
+
+So, fully formed grammar elements (for Python) look like:
+\begin{verbatim}
+main: 'if' '__name__' '==' `literal string` ':' `@body *statement` 'end'
+
+function: 'def' `@identifier identifier **` '(' `@args optional sep ',' identifier **` ')' ':' `@body *statement` 'end'
+
+pass: 'pass'
+
+return: 'return' `@expression expression`
+
+assignment: `@lval identifier **` `@op '='` `@rval boolexpression | expression`
+
+\end{verbatim}
+
+\subsection{AST Transformations}
+
+Transformations to the AST allow for an overall simpler compilation process, reducing the number of construction files required for an output language.
+Essentially, transformations change language-specific features into more generalized ones.
+AST transforms can also model code optimizations.
+
+[Detail of how transformer files work]
+
+\subsection{Constructors}
+
+Constructor files describe how to build generalized syntax features. Mostly, they look like code in the output language, but with the elements replaced with tags from the symbol dictionary.
+i.e. an assignment statement in c++
+\lstset{language=c++}
+\begin{lstlisting}
+auto $lval$ $op$ $rval$
+\end{lstlisting}
+might become
+\lstset{language=c++}
+\begin{lstlisting}
+auto x = 42
+\end{lstlisting}
+However, if we wish to reassign to a variable, the auto type declaration needs to be left off, so we might redefine the constructor file as:
+\begin{verbatim}
+branch defined lval 
+$lval$ $op$ $rval$
+elsebranch
+auto $lval$ $op$ $rval$
+end
+\end{verbatim}
+Where "defined lval" checks if lval is part of the namespace
+How does lval get inserted into the namespace in the first place?
+Constructor files must define which values will be put into the namespace, so our full constructor file would start with:
+\begin{verbatim}
+defines
+lval
+\end{verbatim}
+Additionally, c++ has both header and source files in generation, but assignment statements look the same for each.
+Our full constructor file looks like:
+
+\begin{verbatim}
+defines
+lval
+
+header
+branch defined lval 
+$lval$ $op$ $rval$
+elsebranch
+auto $lval$ $op$ $rval$
+end
+
+source
+branch defined lval 
+$lval$ $op$ $rval$
+elsebranch
+auto $lval$ $op$ $rval$
+end
+\end{verbatim}
+
+Where "header" and "source" are defined in the special cpp/constructors/file file, which outlines which filetypes c++ will construct
+
 % ==================================================
@@
 
-\subsection{Re-implementation of Cython and 2to3}
-Description of implementing these two pieces of software with glossa
+Glossas core focus is on language design and creation. Creation of new languages and extension of existing ones should be very simple.
 
-\subsection{Cython}
-\subsection{2to3}
+\subsection{Glossa as a pre-processor}
 
-\subsection{Comparisons and Benchmarks}
+Since Glossa can convert one language to another, it works as a pre-processor.
+Glossa has the ability for languages to inherit from and extend other languages, so, for example, C++ might inherit from C, and then implement class statements that compile into C code.
+
+\subsection{Language Creation, Design, and Modification}
+
+In its ability to create new languages and extend existing ones, Glossa aims to help programming language research.
+If syntax features can be quickly added or removed, programming languages will evolve more rapidly.
+Rapid development of programming languages leads to better programming languages.
 
 \subsection{Simple code porting}
-Reference work on 2to3, talk about FORTRAN and similar conversions
 
-\subsection{Language Creation}
-Description of implementing new programming languages using glossa
-
-\subsection{Language Design and Modification}
-\subsection{Glossa as a pre-processor}
+Additionally, Glossa is able to port code. For example, Glossa can easily re-implement software like 2to3, which updates old python code.
+For outdated projects, or projects written in too many languages, easy conversions between languages are extremely useful.
 
@@
 
-\subsection{Results Overview}
+% ==================================================
+\section{Conclusion}
+% ==================================================
 
-2to3 comparison
-
-Cython comparison
-
-GHC comparison
-
-\subsection{Quicksort Cython Comparison}
+% ==================================================
+\section{Appendix}
+% ==================================================
 
@@
 
-% ==================================================
-\section{Conclusion}
-% ==================================================
-
 \end{document}

### 2017-03-22 examples/pyfortran/main.f90
Adds python3 constructors for fortran -> python

@@ -1,0 +1,14 @@
+PROGRAM hello 
+    WRITE(*,*) 'Hello World'
+    REAL :: Area_circle
+    IF (1 > 0) THEN
+        WRITE(*,*) 'DANG'
+    ELSE IF (2 < 3) THEN
+        WRITE(*,*) 'DANG'
+    ELSE
+        WRITE(*,*) 'DANG'
+    END IF
+
+    DO WHILE (1 > 2)
+    END DO
+END PROGRAM 

### 2017-03-22 src/gen/generator.cpp

@@ -245,6 +245,7 @@ ElementConstructor<string> Generator::generateSpecialElementConstructor(string l
             else if (keyword == "block") // e.g. block body @;
             {
                 assert(terms.size() == 2 or terms.size() == 3);
+                print(terms[1]);
                 assert(contains(ms_table, terms[1]));
                 auto symbols = ms_table[terms[1]];
                 string formatter = "@";

### 2017-03-22 examples/class/main.py
Adds python3 classes

@@ -2,7 +2,6 @@
 class A():
     def __init__(self):
         print('Created Object')
-        self.x = 2
 
     def foo(self, x):
         print(x*x)

### 2017-04-08 papers/paper.tex
Adds second draft of paper

@@
 
-\title{Fully Generalized Compilation}
+\title{Compilation with Dynamic Grammars}
 \date{01-26-2017}
@@
 Glossa is an investigation into the feasibility of a multi-language source-to-source compiler with dynamic grammars. 
-Assuming that two languages are \textit{isomorphic}, one language can be converted to another if given an adequate description of each language's grammar.
-Given source code in one language, a description of its grammar \textbf{A} , and a description of an output language's grammar \textbf{B}, can \textbf{A} be converted to \textbf{B} such that the output in \textbf{B} is indistinguishable from a program originally written in \textbf{B}?
-Once this is achieved, the grammar description for \textbf{A} can be modified at will, changing \textbf{A}'s syntax, but keeping the \textbf{B} output the same.
+If given an adequate description of each language's grammar, one language can be converted to another if the languages are \textit{isomorphic}.
+If two languages are not \textit{isomorphic}, one can still be converted to another if the non-isomorphisms are solved through an AST transformation.
+For example, C++ can be converted to C if classes are represented as collections of functions that all take a struct as their first argument.
+(Since C++ supports classes, but C does not (non-isomorphism).)
+
+Given source code in one language, a description of its grammar, \textbf{A} , and a description of an output language's grammar \textbf{B}, can \textbf{A} be converted to \textbf{B} such that the output in \textbf{B} is indistinguishable from a program originally written in \textbf{B}, in the same way that the output of Google Translate would look like something written by a native spanish speaker?
+The answer is yes, but there are some limitations. Grammars need to be described fully to Glossa, which is a potentially difficult task.
+The more accurate a grammar description becomes, the more complicated it is to create.
+However, grammar files must be simple, so that they can be created/understood/modified by users.
+Also, the more non-isomorphisms that exist between two programming languages, the less readable the result of a conversion between them will be.
+For example, C++'s class syntax is human-readable, but the C machinery emulating classes is far less readable. 
+This being noted, accurate conversions are 100\% possible if the description files are written properly.
+For description files to be easily written, their syntax should be as intuitive as possible. 
+In Glossa, the description file formats have been refactored several times, so that the current descriptor file syntax is near optimal.
+
+Glossa accomplishes near 100\% conversions for Python3 to C++, as well as Python2 to Python3.
+Glossa has proof of concept conversions for FORTRAN to C++, FORTRAN to Python3, and proof of concept for implementation of a new programming language, Auta.
 
@@
 Glossa provides a \textit{dynamic framework} for easily modifying syntax of input and output languages. 
-As programming paradigms shift, so does language syntax. Ultimately, modifiable syntax leads to better programming languages. 
+Ultimately, modifiable syntax leads to better programming languages.
+As programming paradigms shift, so does syntax. 
+If a language can be changed quickly and easily, then different styles can easily be experimented with, improving the chance of finding an optimal style.
+(i.e.
+A question like "What if C++ used indentation-delimiting instead of braces?" can be tested in an hour or so.
+If someone were to test this, they would likely find that indentation delimiting was clearer than brace delimiting..)
+
 Since each programming language has its own compiler, there is some redundancy in each implementation. 
+For example, the lexer for a C++ compiler and a Java compiler would be extremely similar, since both languages use braces, semicolons, and parentheses in the same way.
+Even two programming languages that don't have similar syntax have similar parts of their compiler. 
+For example, a lexer seperates text based on a list of delimiter-strings, which vary with each programming language.
+The string seperation function, however, is the same for every lexer, and would be redundant across multiple compilers.
+The same concept applies to Parsers and Generators, etc.. (Parsers read tokens and produce an ast, Generators use an AST to generate code)
+
 If programming languages could be compiled with a framework, this redundancy would go away, and programming language researchers would be able to focus on the language itself, as opposed to its compiler.
-
 Essentially, Glossa abstracts the parts of a compiler that don't depend on which language is being compiled, and reads in rules for each language, effectively seperating the language from how it is compiled.
+Because of this, Glossa allows simple implementations of programming languages, which means that Glossa can easily become capable of translating many different languages with ease.
 
@@
 \begin{enumerate}
-\item Code is lexed (seperated into tokens and tagged as keywords, punctuators, literals, etc...)
-\item Tokens are parsed to build an abstract syntax tree (symbolic code representation)
-\item The AST is optimized (i.e. unreachable code is removed, some loops are unrolled)
-\item Machine instructions are generated from AST.
+\item Lexer: Code is lexed (seperated into tokens and tagged as keywords, punctuators, literals, etc...)
+\item Parser: Tokens are parsed to build an Abstract Syntax Tree (symbolic code representation)
+\item Transformer: The AST is optimized (i.e. unreachable code is removed, some loops are unrolled, much more..)
+\item Generator: Machine instructions are generated from AST.
 \end{enumerate}
 
-Glossa differs only slightly from the steps above. Lexing and parsing work as above, but the rules for lexing and parsing respectively are read in at run-time. 
-In the current state of the software, optimizations don't occur, but could easily be modeled as transformations to the abstract syntax tree.
-Instead of generating machine instructions, Glossa generates code in another programming language. (See next page) 
-Instructions for doing this are also read in at run-time.
-While some compilers and interpreters have dynamic ways to modify the syntax of a language, this functionality seems to be unneeded for most compilers.
-Because of its dynamic nature, it is very simple to have Glossa support multiple programming languages both for input and output.
+Glossa does exactly the same, but, instead of using hardcoded functions, Glossa creates a Lexer, Parser, Transformer and Generator during the compilation phase by reading in descriptions of the languages being translated.
+
+Assuming conversion from \textbf{A} to \textbf{B}, as in the Abstract, Glossa creates the Lexer, Parser, and Transformer based on \textbf{A}, and the Generator based on \textbf{B}.
+As one would expect, this means that Glossa has four types of descriptor files:
+
+\begin{enumerate}
+    \item \textit{lex files}: A list of strings that constitute atomic types like string literals, operators, keywords 
+    \item \textit{grammar files}: A description of a parser for each grammar element in language \textbf{A} 
+    \item \textit{constructor files}: A description of a generator for each grammar element in language \textbf{B}
+    \item \textit{transformer files}: A description of transformations for each grammar element in language \textbf{A}.
+\end{enumerate}
+
+The next page has a diagram of compilation in Glossa, utilizing these four file types to create the Lexer, Parser, Transformer, and Generator.
 
@@
     \node (sourcea) [startstop]                       {Source Code A};
-    \node (lexer)   [process, below of=sourcea] {Lexical Analyzer};
+    \node (lexer)   [process, below of=sourcea]       {Lexer};
     \node (tokens)  [io, below of=lexer]              {Symbolic Tokens};
+    \node (lrules)  [process, right of=lexer, xshift=2cm]  {Lex Rules};
+    \node (lfiles)  [io, right of=lrules, xshift=2cm]  {Lex Files};
     \node (parser)  [process, below of=tokens]        {Parser};
     \node (asta)    [io, below of=parser]             {AST};
+    \node (grules)  [process, right of=parser, xshift=2cm]  {Grammar Rules};
+    \node (gfiles)  [io, right of=grules, xshift=2cm] {Grammar Files};
     \node (trans)   [process, below of=asta]          {Transformer};
     \node (astb)    [io, below of=trans]              {Intermediate AST};
+    \node (trules)  [process, right of=trans, xshift=2cm]  {Transformer Rules};
+    \node (tfiles)  [io, right of=trules, xshift=2cm]  {Transformer Files};
     \node (gen)     [process, below of=astb]          {Generator};
     \node (stop)    [startstop, below of=gen]         {Source Code B};
+    \node (ggrules) [process, right of=gen, xshift=2cm]  {Generator Rules};
+    \node (ggfiles) [io, right of=ggrules, xshift=2cm]    {Generator Files};
 
@@
     \draw [arrow] (lexer) -- (tokens);
+    \draw [arrow] (lfiles) -- (lrules);
+    \draw [arrow] (lrules) -- (lexer);
     \draw [arrow] (tokens) -- (parser);
+    \draw [arrow] (gfiles) -- (grules);
+    \draw [arrow] (grules) -- (parser);
     \draw [arrow] (parser) -- (asta);
     \draw [arrow] (asta) -- (trans);
+    \draw [arrow] (tfiles) -- (trules);
+    \draw [arrow] (trules) -- (trans);
     \draw [arrow] (trans) -- (astb);
     \draw [arrow] (astb) -- (gen);
+    \draw [arrow] (ggfiles) -- (ggrules);
+    \draw [arrow] (ggrules) -- (gen);
     \draw [arrow] (gen) -- (stop);
+
+    % title
+    \node[align=center,font=\bfseries, yshift=2em] (title) 
+	at (current bounding box.north)
+	{Compilation in Glossa};
 
@@
 
-\subsection{Abstracting Language Definitions}
+\subsection{Lex Files}
 
-To parse an input language, Glossa needs a description of the languages grammar, which is provided through a \textit{grammar file}.
-Optional descriptions of AST transformations are provided through \textit{transformer files}.
+Lex files are the most straightforward of all of Glossa's descriptor files.
 
-To generate an output language from an AST, Glossa needs a set of \textit{constructor files}.
+A language's lex directory contains the following files:
+\begin{verbatim}
+comment_delimiters  logicaloperators  operators  punctuators  string_delimiters  whitespace
+\end{verbatim}
+
+The files 
+\begin{verbatim}
+logicaloperators operators punctuators string_delimiters
+\end{verbatim}
+are each just lists of strings
+
+The 
+\begin{verbatim}
+comment_delimiters  
+\end{verbatim}
+file is a two-line file of the form:
+\begin{verbatim}
+#
+""" 
+\end{verbatim}
+In General:
+\begin{verbatim}
+Single line comment delim
+Multi line comment delim
+\end{verbatim}
+
+An example whitespace file:
+\begin{verbatim}
+indent  false
+space   false
+newline false
+\end{verbatim}
+Where "false" says if a whitespace element should be kept as a token when the language is lexed.
 
@@
 
-Glossa's parse operation can be modeled as a function with the signature:
+Glossa's parse operation converts a list of tokens to an AST.
 
+Glossa will attempt to identify remaining tokens with high-level statement types, which in turn use lower-level grammar types:
 \begin{verbatim}
-parse :: Tokens -> AST
+statement: `@statement a | b | c`
 \end{verbatim}
-
-Where the body of the parse function looks like:
-
-\lstset{language=Python}
-\begin{lstlisting}
-while not tokens.empty():
-    identify_remaining(tokens)
-\end{lstlisting}
-
-Glossa will attempt to identify remaining tokens with any of the high-level statement types provided.
-These statement types can use other grammar constructs as well
+Where a might be:
+\begin{verbatim}
+a: `@val d | e`
+\end{verbatim}
 
@@
 \begin{verbatim}
-name: `first_element` `second_element`
+name: `first_element` `second_element` .. `last_element`
+or
+name: `option_a` | `option_b` ..  | `option_c`
 \end{verbatim}
 
-Where first\_element and second\_element are parsers of the form:
+Where each element is a parser of the form:
 
-\begin{verbatim}
 an optional "@name" tag, which saves the result of the parser to the symbol dictionary under "name"
 Either:
+\begin{verbatim}
 - A subtype parser (i.e `'='`),
@@
 - A link to another grammar element (i.e. `value`)
+\end{verbatim}
 
 So, the following are all examples of valid parsers:
+\begin{verbatim}
 `@val value`          // Link to value type, saved as "val"
@@
 `@name identifier **` // Any identifier saved as "name"
+\end{verbatim}
 
-However, these parsers can be prefixed with the following keywords to change their meaning:
+However, these parsers can be prefixed with the following 
+  keywords to change their meaning:
 
+\begin{verbatim}
 !           : discard the parse result of this parser
@@
 */many      : parse the parser several times until it fails
-many1       : parse the parser several times, requiring it to parse successfully at least once
+many1       : parse the parser several times, requiring it to parse successfully 
+                at least once.
 optional    : make a parser optional
@@
 sep a b     : parse bs seperated by as (i.e. sep , value) 
+\end{verbatim}
 
-Some examples of more sophisticated parsers
+Some examples of more sophisticated parsers:
 
+\begin{verbatim}
 `@statement import_from | main | ... ` 
@@
 
-function: 'def' `@identifier identifier **` '(' `@args optional sep ',' identifier **` ')' ':' `@body *statement` 'end'
+function: 'def' `@identifier identifier **` 
+    '(' `@args optional sep ',' identifier **` ')' ':' 
+    `@body *statement` 'end'
 
@@
 assignment: `@lval identifier **` `@op '='` `@rval boolexpression | expression`
-
 \end{verbatim}
-
-\subsection{AST Transformations}
-
-Transformations to the AST allow for an overall simpler compilation process, reducing the number of construction files required for an output language.
-Essentially, transformations change language-specific features into more generalized ones.
-AST transforms can also model code optimizations.
-
-[Detail of how transformer files work]
 
@@
 
+\subsection{Transformer Files}
+
+Transformations to the AST allow for an overall simpler compilation process, reducing the number of construction files required for an output language. 
+AST transformations also solve non-isomorphisms, which is very useful if two languages are not very similar.
+
+Essentially, transformations change language-specific features into more generalized ones. 
+AST transforms can also model code optimizations.
+
+Each element of the AST is MultiSymbol, which is a tag (string), and a string dictionary of symbols.
+To transform an AST element, the tag can be changed, or elements within the string dictionary can be manipulated.
+
+A transformer file is just a series of these transformations:
+\begin{verbatim}
+add    key (literal | identifier | ..) (2 | x | ...)
+append key (literal | identifier | ..) (2 | x | ...)
+copy   key1 key2
+move   key1 key2
+copy-append key1 key2
+move-append key1 key2
+retag newtag
+\end{verbatim}
+Which can be surrounded by control flow, in the same way that constructor files can:
+\begin{verbatim}
+branch defined identifier 
+move identifier old_identifier
+add name identifier f
+elsebranch
+add name identifier f
+end
+\end{verbatim}
+(This AST transform renames the syntax element to f, saving the old name to the key "old\_identifier"
+
 % ==================================================
@@
 
-Glossas core focus is on language design and creation. Creation of new languages and extension of existing ones should be very simple.
+Glossa has two core applications: Translation of code, and programming language design.
 
-\subsection{Glossa as a pre-processor}
+\subsection{Translation}
 
+If Glossa has adequate language descriptions, then translations are trivial. 
 Since Glossa can convert one language to another, it works as a pre-processor.
@@
 
-\subsection{Language Creation, Design, and Modification}
+\subsection{Language Design}
 
-In its ability to create new languages and extend existing ones, Glossa aims to help programming language research.
-If syntax features can be quickly added or removed, programming languages will evolve more rapidly.
-Rapid development of programming languages leads to better programming languages.
+Since Glossa uses dynamic language descriptions, languages can easily be created or modified by changing their descriptor files.
+Glossa also allows languages to inherit from existing languages.
+For example, Glossa's descriptions for C++ might inherit from C, and only overwrite or add features.
+This functionality makes language experimentation painless, as code doesn't even need to be recompiled.
 
-\subsection{Simple code porting}
+Glossa provides examples of the following translations:
+\begin{enumerate}
+    \item Python3 -\textgreater C++
+    \item Python2 -\textgreater C++ 
+    \item Python2 -\textgreater Python3
+    \item FORTRAN -\textgreater C++ 
+    \item FORTRAN -\textgreater Python3 
+\end{enumerate}
+Glossa also has an example of a language implementation: Auta, which provides a simple automation-scripting interface, by building an API into the languages syntax:
 
-Additionally, Glossa is able to port code. For example, Glossa can easily re-implement software like 2to3, which updates old python code.
-For outdated projects, or projects written in too many languages, easy conversions between languages are extremely useful.
+\lstset{language=Python}
+\begin{lstlisting}
+every Tuesday:
+    send_email(team_a, “Meeting in room 1024 @ 2:00”)
+every week:
+    i = download_spreadsheet(“weekly income”)
+    out = calc_taxes(i)
+    upload_spreadsheet(out)
+\end{lstlisting}
+Which would compile to several Google-API calls in Python, which would be much more complicated. 
+Simplifying the API calls by building them into Auta's syntax allows a layperson to write simple scripts.
+
+This example isn't necessarily meant to be an actual programming language, but more to show how a language could easily be implemented in Glossa.
 
@@
 
+Recall the current suite of translation examples:
+\begin{enumerate}
+    \item Python3 -\textgreater C++
+    \item Python2 -\textgreater C++ 
+    \item Python2 -\textgreater Python3
+    \item FORTRAN -\textgreater C++ 
+    \item FORTRAN -\textgreater Python3 
+\end{enumerate}
+
+Glossa's support for the different versions of Python and C++ output are significantly developed, supporting 80-90\% of the syntax for each language. 
+Glossa's support for FORTRAN is more experimental, but 100\% support would be trivial to add, since FORTRAN has very simple syntax.
+Glossa could currently support more complex input languages, like C++ or Haskell, but the description files would be more difficult to write.
+
+For language design, Glossa is fully equipped. The only restriction is the time required to write description files.
+
 % ==================================================
@@
 % ==================================================
+
+Glossa shows that a multi-language source to source compiler is possible. 
+While Glossa only supports a few different languages, it could easily support more if more description files were written.
+However, Glossa's interface would benefit from simplification, since writing description files is a hard task. Also, even in description files, there is some redundancy that could be eliminated.
+
+Glossa has accomplished far more than it originally set out to: Perhaps the software will mature in the future, and eventually be used at the industry level.
 

### 2017-04-14 papers/paper.tex
Third? draft of paper

@@
 % ==================================================
-Glossa is an investigation into the feasibility of a multi-language source-to-source compiler with dynamic grammars. 
+Glossa is both a multi-language source to source compiler and, by extension, a framework for creating compilers.
+Glossa's main goal is to convert any programming language \textbf{A} to any programming language \textbf{B}, such that the output in \textbf{B} is indistinguishable from code written by a native \textbf{B} programmer, in the same way that the output from Google Translate would ideally look as if it were written by a native speaker.
 If given an adequate description of each language's grammar, one language can be converted to another if the languages are \textit{isomorphic}.
@@
 For example, C++ can be converted to C if classes are represented as collections of functions that all take a struct as their first argument.
-(Since C++ supports classes, but C does not (non-isomorphism).)
+(Since C++ supports classes, but C does not (an example of a non-isomorphism).)
+However, solving non-isomorphisms through AST transformations potentially compromises output code readability.
+This being noted, a human making the conversion would also have to compromise readability, since there \textit{is no other way to retain functionality.} So, when it has to, Glossa compromises output code readability for proper functionality.
 
-Given source code in one language, a description of its grammar, \textbf{A} , and a description of an output language's grammar \textbf{B}, can \textbf{A} be converted to \textbf{B} such that the output in \textbf{B} is indistinguishable from a program originally written in \textbf{B}, in the same way that the output of Google Translate would look like something written by a native spanish speaker?
-The answer is yes, but there are some limitations. Grammars need to be described fully to Glossa, which is a potentially difficult task.
+Glossa has several caveats. 
+Grammars need to be described fully to Glossa, which is potentially difficult.
 The more accurate a grammar description becomes, the more complicated it is to create.
@@
 Also, the more non-isomorphisms that exist between two programming languages, the less readable the result of a conversion between them will be.
-For example, C++'s class syntax is human-readable, but the C machinery emulating classes is far less readable. 
 This being noted, accurate conversions are 100\% possible if the description files are written properly.
@@
 Glossa has proof of concept conversions for FORTRAN to C++, FORTRAN to Python3, and proof of concept for implementation of a new programming language, Auta.
+While the software is still in its infancy, the core concepts have been proven, indicating that an industry level multi-language source to source compiler is possible.
 
@@
 
-Glossa provides a \textit{dynamic framework} for easily modifying syntax of input and output languages. 
+Since Glossa aims to be capable of translating many different programming languages, it must provide a dynamic framework for easily modifying syntax of input and output languages. 
+In addition to letting Glossa translate existing languages, this functionality makes implementing new programming languages very simple.
+
+\textbf{EDITING POINT}
+
 Ultimately, modifiable syntax leads to better programming languages.
@@
 
-Glossa provides examples of the following translations:
-\begin{enumerate}
-    \item Python3 -\textgreater C++
-    \item Python2 -\textgreater C++ 
-    \item Python2 -\textgreater Python3
-    \item FORTRAN -\textgreater C++ 
-    \item FORTRAN -\textgreater Python3 
-\end{enumerate}
-Glossa also has an example of a language implementation: Auta, which provides a simple automation-scripting interface, by building an API into the languages syntax:
-
-\lstset{language=Python}
-\begin{lstlisting}
-every Tuesday:
-    send_email(team_a, “Meeting in room 1024 @ 2:00”)
-every week:
-    i = download_spreadsheet(“weekly income”)
-    out = calc_taxes(i)
-    upload_spreadsheet(out)
-\end{lstlisting}
-Which would compile to several Google-API calls in Python, which would be much more complicated. 
-Simplifying the API calls by building them into Auta's syntax allows a layperson to write simple scripts.
-
-This example isn't necessarily meant to be an actual programming language, but more to show how a language could easily be implemented in Glossa.
-
 % ==================================================
@@
 
+\subsection{Language Design}
+
+As discussed in the Applications section, dynamic grammars simplify language creation.
+For example, Glossa ships with an experimental language, Auta, which extends the Python3 programming language by adding common tasks, like download spreadsheets or sending emails, to the language's syntax:
+
+\lstset{language=Python}
+\begin{lstlisting}
+every Tuesday:
+    send_email(team_a, “Meeting in room 1024 @ 2:00”)
+every week:
+    i = download_spreadsheet(“weekly income”)
+    out = calc_taxes(i)
+    upload_spreadsheet(out)
+\end{lstlisting}
+Which would compile to several Google-API calls in Python, which would be much more complicated. 
+Simplifying the API calls by building them into Auta's syntax allows a layperson to write simple scripts.
+
+This example isn't necessarily meant to be an actual programming language, but more to show how a language could easily be implemented in Glossa.
+
 % ==================================================
@@
 Glossa shows that a multi-language source to source compiler is possible. 
+Since description files are the only pre-requisite for translating a particular language, Glossa can theoretically translate any language, as long as a description is provided.
 While Glossa only supports a few different languages, it could easily support more if more description files were written.

### 2017-04-15 src/gen/read.cpp
Adds register transform to AST trans features

@@ -55,7 +55,6 @@ ConditionEvaluator generateConditionEvaluator(vector<string> terms)
         return [terms](unordered_set<string>& names, MultiSymbolTable& ms_table)
         {
             auto id = terms[1];
-            //print(id);
             assert(contains(ms_table, id));
             return not ms_table[id].empty();
         };

### 2017-04-15 src/transform/transformer.cpp

@@ -45,19 +45,27 @@ void Transformer::operator()(IdentifiedGroups& identified_groups)
     }
 }
 
-void Transformer::_keyword_transform(vector<string>& terms, string& tag, MultiSymbolTable& ms_table)
+void Transformer::_keyword_transform(vector<string>& terms, 
+                                     string& otag, 
+                                     MultiSymbolTable& oms_table,
+                                     string& reg_tag,
+                                     MultiSymbolTable& reg_ms_table)
 {
     assert(not terms.empty());
     auto keyword = terms[0];
-    if (keyword == "add" or keyword == "append")
+    bool reg = contains(keyword, "reg");
+    auto &ms_table = reg ? reg_ms_table : oms_table;
+    auto &tag      = reg ? reg_tag      : otag; 
+    if (contains(keyword, "add") or contains(keyword, "append"))
     {
         assert(terms.size() == 4);
         auto creator = syntax::generatorMap.at(terms[2]);
         auto symbol  = creator({terms[3]});
-        if (keyword == "add" or not contains(ms_table, terms[1]))
+        if (contains(keyword, "add") or not contains(ms_table, terms[1]))
         {
-            assert(not contains(ms_table, terms[1]));
+            assert(not contains(ms_table, terms[1])); // If "add" branch
             ms_table[terms[1]] = vector<shared_ptr<Symbol>>({symbol});
+            auto s = make_shared<MultiSymbol>(MultiSymbol(reg_tag, reg_ms_table));
         }
         else
         {
@@ -84,10 +92,26 @@ void Transformer::_keyword_transform(vector<string>& terms, string& tag, MultiSy
             ms_table.erase(a);
         }
     }
-    else if (keyword == "retag")
+    else if (contains(keyword, "retag"))
     {
         assert(terms.size() == 2);
         tag = terms[1];
+    }
+    else if (contains(keyword, "pushback"))
+    {
+        assert(terms.size() == 2);
+        auto symbol = make_shared<MultiSymbol>(MultiSymbol(reg_tag, reg_ms_table));
+        if (contains(keyword, "override") or not contains(oms_table, terms[1]))
+        {
+            oms_table[terms[1]] = vector<shared_ptr<Symbol>>({symbol});
+        }
+        else
+        {
+            oms_table[terms[1]].push_back(symbol);
+        }
+        // Reset
+        reg_tag = "";
+        reg_ms_table = MultiSymbolTable();
     }
     else
     {
[…]

### 2017-04-17 papers/paper.tex
Adds minor edits to 2nd draft of paper

@@
 In addition to letting Glossa translate existing languages, this functionality makes implementing new programming languages very simple.
-
-\textbf{EDITING POINT}
 
@@
 Glossa's support for the different versions of Python and C++ output are significantly developed, supporting 80-90\% of the syntax for each language. 
-Glossa's support for FORTRAN is more experimental, but 100\% support would be trivial to add, since FORTRAN has very simple syntax.
+However, support for FORTRAN is more experimental, but 100\% support would be trivial to add, since FORTRAN has very simple syntax.
 Glossa could currently support more complex input languages, like C++ or Haskell, but the description files would be more difficult to write.
@@
 
-Glossa has accomplished far more than it originally set out to: Perhaps the software will mature in the future, and eventually be used at the industry level.
+However, Glossa in its current form is not intended to be industrial-level software. 
+Instead, it is an investigation into creating a generalized compilation system that does not hardcore any rules. 
+While Glossa is useful at doing \textit{some} automated translations, it is likely more useful for implementing new programming languages.
+Because of the generalizations (discarding of hard-coded rules) that Glossa makes, changing language definitions is trivial compared to the difficulty of modifying the source of a compiler.
+
+Glossa has accomplished far more than it originally set out to: Perhaps Glossa can be used as groundwork for an industrial-level compiler framework.
 

### 2017-04-18 src/transform/transformer.cpp
Removes old langs, extends natural_java syntax

@@ -56,7 +56,23 @@ void Transformer::_keyword_transform(vector<string>& terms,
     bool reg = contains(keyword, "reg");
     auto &ms_table = reg ? reg_ms_table : oms_table;
     auto &tag      = reg ? reg_tag      : otag; 
-    if (contains(keyword, "add") or contains(keyword, "append"))
+    if (contains(keyword, "transfer"))
+    {
+        assert(terms.size() == 3);
+        auto a = terms[1];
+        auto b = terms[2];
+        assert(contains(oms_table, a));
+        if (contains(keyword, "append"))
+        {
+            assert(contains(reg_ms_table, b));
+            concat(reg_ms_table[b], oms_table[a]);
+        }
+        else
+        {
+            reg_ms_table[b] = oms_table[a];
+        }
+    }
+    else if (contains(keyword, "add") or contains(keyword, "append"))
     {
         assert(terms.size() == 4);
         auto creator = syntax::generatorMap.at(terms[2]);
@@ -112,6 +128,10 @@ void Transformer::_keyword_transform(vector<string>& terms,
         // Reset
         reg_tag = "";
         reg_ms_table = MultiSymbolTable();
+    }
+    else if (contains(keyword, "delete"))
+    {
+        ms_table.erase(terms[1]);
     }
     else
     {

### 2017-04-18 src/gen/generator.cpp
Adds minor reporting tools

@@ -14,6 +14,7 @@ Generator::Generator(vector<string> filenames, string directory)
     readStructureFile(directory + "file");
     for (auto filename : filenames)
     {
+        print("Loading constructor " + filename);
         construction_map[filename] = readConstructor(directory + filename);
     }
     ec_creator = [this](string s){ return this->generateElementConstructor(s);}; 
@@ -99,7 +100,7 @@ vector<tuple<string, string, vector<string>>> Generator::operator()(unordered_se
     vector<tuple<string, Constructor<string>>> constructors;
     if (not contains(construction_map, symbol_type))
     {
-        assert(ms_table.size() == 1);
+        err_if(ms_table.size() != 1, "\"" + symbol_type + "\" is not in the construction map and cannot be built using a default constructor (id)");
         for (auto fc : file_constructors)
         {
             auto filetype = get<0>(fc);
@@ -289,7 +290,7 @@ ElementConstructor<string> Generator::generateSpecialElementConstructor(string l
  */
 string Generator::formatSymbol (string s, unordered_set<string>& names, MultiSymbolTable& ms_table, string filetype, vector<string>& definitions)
 {
-    assert(contains(ms_table, s));
+    err_if(not contains(ms_table, s), s + " is not in the symbol table");
     auto ms_group = ms_table[s];         
     assert(ms_group.size() == 1);
 

### 2017-04-18 src/tools/base.hpp

@@ -49,7 +49,6 @@ private:
     std::string name;
 };
 
-void exception_assert(bool b);
 
 /** 
  * Resizes a vector using iterator based constructors
@@ -130,4 +129,8 @@ static inline std::string &rtrim(std::string &s)
     std::not1(std::ptr_fun<int, int>(std::isspace))).base(), s.end());
     return s;
 }
+
+
+void err_if(bool b, string &&s);
+void err_if(bool b, string &s);
 }

### 2017-04-18 src/compiler.cpp
Adds dual-transform (AST universality!)

@@ -83,11 +83,11 @@ namespace compiler
      * @param language Language for code generator to be loaded for
      * @return Transformer which can transformer AST for the given language
      */
-    Transformer loadTransformer(string language)
+    Transformer loadTransformer(string language, string prefix)
     {
         print("Loading transformers for " + language);
         auto transformer_files = readFile("languages/" + language + "/transformers/core");
-        auto transformer = Transformer(transformer_files, "languages/" + language + "/transformers/");
+        auto transformer = Transformer(transformer_files, "languages/" + language + "/" + prefix + "transformers/");
         print("Done");
         return transformer;
     }
@@ -107,7 +107,8 @@ namespace compiler
         auto grammar     = loadGrammar(input_lang);
         auto generator   = loadGenerator(output_lang);
         auto lexmap      = buildLexMap("languages/" + input_lang + "/lex/", grammar.keywords);
-        auto transformer = loadTransformer(input_lang);
+        auto pre_transformer  = loadTransformer(input_lang,  "pre_");
+        auto post_transformer = loadTransformer(output_lang, "post_");
         
 
         auto symbol_table = readSymbolTable("languages/symboltables/" + input_lang + output_lang);
@@ -118,7 +119,7 @@ namespace compiler
         {
             try
             {
-                compile(file, grammar, generator, lexmap, transformer, symbol_table, input_dir, output_dir, logger);
+                compile(file, grammar, generator, lexmap, pre_transformer, post_transformer, symbol_table, input_dir, output_dir, logger);
             }
             catch(...)
             {
@@ -140,7 +141,8 @@ namespace compiler
      * @param logger           OutputManager class for managing verbose output. Use instead of print() calls
      */
     void compile(string filename, Grammar& grammar, Generator& generator, LexMap& lexmap,
-                 Transformer& transformer,
+                 Transformer& pre_transformer,
+                 Transformer& post_transformer,
                  unordered_map<string, string>& symbol_table, string input_directory, 
                  string output_directory, OutputManager logger)
     {
@@ -158,10 +160,13 @@ namespace compiler
         }
         logger.log("Identifying tokens from grammar:");
         auto identified_groups = grammar.identifyGroups(joined_tokens, logger);
-        logger.log("Identified groups AST:");
+        logger.log("Initial AST:");
         showAST(identified_groups, logger);
-        logger.log("Transformed (intermediate) AST:");
-        transformer(identified_groups);
+        logger.log("Universal AST:");
[…]

### 2017-04-18 src/compiler.cpp
WIP add multi-register transforms

@@ -86,7 +86,7 @@ namespace compiler
     Transformer loadTransformer(string language, string prefix)
     {
         print("Loading transformers for " + language);
-        auto transformer_files = readFile("languages/" + language + "/transformers/core");
+        auto transformer_files = readFile("languages/" + language + "/" + prefix + "transformers/core");
         auto transformer = Transformer(transformer_files, "languages/" + language + "/" + prefix + "transformers/");
         print("Done");
         return transformer;

### 2017-04-18 src/transform/transformer.cpp

@@ -48,20 +48,43 @@ void Transformer::operator()(IdentifiedGroups& identified_groups)
 void Transformer::_keyword_transform(vector<string>& terms, 
                                      string& otag, 
                                      MultiSymbolTable& oms_table,
-                                     string& reg_tag,
-                                     MultiSymbolTable& reg_ms_table)
+                                     RegisterMap& register_map)
 {
     assert(not terms.empty());
     auto keyword = terms[0];
-    bool reg = contains(keyword, "reg");
-    auto &ms_table = reg ? reg_ms_table : oms_table;
-    auto &tag      = reg ? reg_tag      : otag; 
+
+    if (keyword == "createreg")
+    {
+        assert(terms.size() == 2);
+        register_map[terms[1]] = make_tuple("", MultiSymbolTable());
+        return;
+    }
+
+    MultiSymbolTable& ms_table = oms_table;
+    string&           tag      = otag;
+    if (keyword == "reg")
+    {
+        assert(terms.size() > 2);
+        auto reg_name = terms[1];
+        err_if(not contains(register_map, reg_name), "Register " + reg_name + " not found");
+        auto& reg_tuple = register_map[reg_name];
+        terms = slice(terms, 2);
+        tag      = get<0>(reg_tuple);
+        ms_table = get<1>(reg_tuple);
+    }
+
+    keyword = terms[0];
     if (contains(keyword, "transfer"))
     {
-        assert(terms.size() == 3);
-        auto a = terms[1];
-        auto b = terms[2];
-        assert(contains(oms_table, a));
+        assert(terms.size() == 4);
+
+        auto reg_name = terms[1];
+        err_if(not contains(register_map, reg_name), "Register " + reg_name + " not found");
+        auto a = terms[2];
+        auto b = terms[3];
+        err_if(not contains(oms_table, a), a + " not in original table");
+        auto& reg_ms_table = get<1>(register_map[reg_name]);
+
         if (contains(keyword, "append"))
         {
             assert(contains(reg_ms_table, b));
@@ -81,7 +104,6 @@ void Transformer::_keyword_transform(vector<string>& terms,
         {
             assert(not contains(ms_table, terms[1])); // If "add" branch
             ms_table[terms[1]] = vector<shared_ptr<Symbol>>({symbol});
-            auto s = make_shared<MultiSymbol>(MultiSymbol(reg_tag, reg_ms_table));
         }
         else
         {
[…]

### 2017-04-18 src/transform/transformer.hpp

@@ -8,6 +8,9 @@ namespace transform
 using namespace gen;
 using namespace grammar;
 
+using Register    = tuple<string, MultiSymbolTable>;
+using RegisterMap = unordered_map<string, Register>; 
+
 template <typename T>
 Constructor<T> generateTransformConstructor(vector<string> content,
         ElementConstructorCreator<T>  ec_creator)
@@ -33,8 +36,7 @@ private:
     void _keyword_transform(vector<string>& terms, 
                             string& otag, 
                             MultiSymbolTable& oms_table,
-                            string& reg_tag,
-                            MultiSymbolTable& reg_ms_table);
+                            RegisterMap& register_map);
 
 };
 

### 2017-04-18 src/transform/transformer.cpp
Adds multiple-register capable transforms

@@ -60,8 +60,6 @@ void Transformer::_keyword_transform(vector<string>& terms,
         return;
     }
 
-    MultiSymbolTable& ms_table = oms_table;
-    string&           tag      = otag;
     if (keyword == "reg")
     {
         assert(terms.size() > 2);
@@ -69,8 +67,10 @@ void Transformer::_keyword_transform(vector<string>& terms,
         err_if(not contains(register_map, reg_name), "Register " + reg_name + " not found");
         auto& reg_tuple = register_map[reg_name];
         terms = slice(terms, 2);
-        tag      = get<0>(reg_tuple);
-        ms_table = get<1>(reg_tuple);
+        auto& reg_tag      = get<0>(reg_tuple);
+        auto& reg_ms_table = get<1>(reg_tuple);
+        _keyword_transform(terms, reg_tag, reg_ms_table, register_map);
+        return;
     }
 
     keyword = terms[0];
@@ -80,11 +80,11 @@ void Transformer::_keyword_transform(vector<string>& terms,
 
         auto reg_name = terms[1];
         err_if(not contains(register_map, reg_name), "Register " + reg_name + " not found");
+        auto& reg_ms_table = get<1>(register_map[reg_name]);
+
         auto a = terms[2];
         auto b = terms[3];
         err_if(not contains(oms_table, a), a + " not in original table");
-        auto& reg_ms_table = get<1>(register_map[reg_name]);
-
         if (contains(keyword, "append"))
         {
             assert(contains(reg_ms_table, b));
@@ -100,14 +100,14 @@ void Transformer::_keyword_transform(vector<string>& terms,
         assert(terms.size() == 4);
         auto creator = syntax::generatorMap.at(terms[2]);
         auto symbol  = creator({terms[3]});
-        if (contains(keyword, "add") or not contains(ms_table, terms[1]))
+        if (contains(keyword, "add") or not contains(oms_table, terms[1]))
         {
-            assert(not contains(ms_table, terms[1])); // If "add" branch
-            ms_table[terms[1]] = vector<shared_ptr<Symbol>>({symbol});
+            assert(not contains(oms_table, terms[1])); // If "add" branch
+            oms_table[terms[1]] = vector<shared_ptr<Symbol>>({symbol});
         }
         else
         {
-            ms_table[terms[1]].push_back(symbol);
+            oms_table[terms[1]].push_back(symbol);
         }
     }
     else if (contains(keyword, "copy") or contains(keyword, "move"))
[…]

### 2017-04-18 src/transform/transformer.cpp
Refactors multi-reg transform, removing dup code

@@ -52,6 +52,12 @@ void Transformer::_keyword_transform(vector<string>& terms,
 {
     assert(not terms.empty());
     auto keyword = terms[0];
+    bool reg = keyword == "reg" or contains(keyword, "transfer") or contains(keyword, "pushback");
+    assert(terms.size() >= 2);
+    auto reg_name = reg ? terms[1] : "";
+    if (reg) err_if(not contains(register_map, reg_name), "Register " + reg_name + " not found");
+    auto& reg_tag      = reg ? get<0>(register_map[reg_name]) : otag;
+    auto& reg_ms_table = reg ? get<1>(register_map[reg_name]) : oms_table;
 
     if (keyword == "createreg")
     {
@@ -59,29 +65,15 @@ void Transformer::_keyword_transform(vector<string>& terms,
         register_map[terms[1]] = make_tuple("", MultiSymbolTable());
         return;
     }
-
-    if (keyword == "reg")
+    else if (keyword == "reg")
     {
-        assert(terms.size() > 2);
-        auto reg_name = terms[1];
-        err_if(not contains(register_map, reg_name), "Register " + reg_name + " not found");
-        auto& reg_tuple = register_map[reg_name];
         terms = slice(terms, 2);
-        auto& reg_tag      = get<0>(reg_tuple);
-        auto& reg_ms_table = get<1>(reg_tuple);
         _keyword_transform(terms, reg_tag, reg_ms_table, register_map);
         return;
     }
-
-    keyword = terms[0];
-    if (contains(keyword, "transfer"))
+    else if (contains(keyword, "transfer"))
     {
         assert(terms.size() == 4);
-
-        auto reg_name = terms[1];
-        err_if(not contains(register_map, reg_name), "Register " + reg_name + " not found");
-        auto& reg_ms_table = get<1>(register_map[reg_name]);
-
         auto a = terms[2];
         auto b = terms[3];
         err_if(not contains(oms_table, a), a + " not in original table");
@@ -138,12 +130,7 @@ void Transformer::_keyword_transform(vector<string>& terms,
     else if (contains(keyword, "pushback"))
     {
         assert(terms.size() == 3);
-        auto reg_name = terms[1];
         auto key      = terms[2];
-        err_if(not contains(register_map, reg_name), "Register " + reg_name + " not found");
-        auto& reg_tuple    = register_map[reg_name];
-        auto& reg_tag      = get<0>(reg_tuple);
[…]

### 2017-04-18 examples/pyfortran/main.f90
Adds FORTRAN indexed loops

@@ -24,4 +24,13 @@ PROGRAM hello
         CASE DEFAULT
     END SELECT
 
+    ! All nums from one to ten
+    DO i = 0 10 
+        WRITE(*,*) i
+    END DO
+    ! Even nums from one to ten
+    DO i = 0 10 2
+        WRITE(*,*) i
+    END DO
+
 END PROGRAM 

### 2017-04-18 examples/pyfortran/main.f90
Adds FORTRAN infinite loops

@@ -33,4 +33,9 @@ PROGRAM hello
         WRITE(*,*) i
     END DO
 
+    DO
+        WRITE(*,*) "Looping infinitely"
+        1 < 2 EXIT
+    END DO
+
 END PROGRAM 

### 2017-04-18 examples/pyfortran/main.f90
Adds multi-dimensional FORTRAN arrays

@@ -38,4 +38,7 @@ PROGRAM hello
         1 < 2 EXIT
     END DO
 
+    INTEGER, DIMENSION(10) :: A
+    INTEGER, DIMENSION(10, 10) :: B
+
 END PROGRAM 

### 2017-04-19 demo.py
Adds FORTRAN style array initialization

@@ -115,7 +115,7 @@ def transpile(demoname, demos, verbosity, runcomp=False, runlang=True):
         directory = l[0]
         languageargs = l[1:]
         build(directory, languageargs, verbosity)
-        if languageargs[0] in ['python2', 'python3', 'auta']:
+        if languageargs[0] in ['python2', 'python3', 'auta', 'fortran']:
             if os.path.exists('output/__pylib__'):
                 shutil.rmtree('output/__pylib__')
             shutil.copytree('std/__pylib__/', 'output/__pylib__')

### 2017-04-19 examples/pyfortran/main.f90

@@ -38,7 +38,13 @@ PROGRAM hello
         1 < 2 EXIT
     END DO
 
-    INTEGER, DIMENSION(10) :: A
-    INTEGER, DIMENSION(10, 10) :: B
+    INTEGER, DIMENSION(4) :: A
+    WRITE(*,*) A
+    A = (/1, 2, 3, 4/)
+    WRITE(*,*) A
+    INTEGER, DIMENSION(2, 4) :: B
+    WRITE(*,*) B
+    B = (/1, 2, 3, 4, 5, 6, 7, 8/)
+    WRITE(*,*) B
 
 END PROGRAM 

### 2017-04-19 std/__pylib__/__init__.py

@@ -4,3 +4,4 @@ from .gmail import send_gmail
 from .utilities import *
 from .chrono    import every 
 
+from .arrays import *

### 2017-04-22 papers/paper.tex
Adds paper/notes, third draft

--- 2017-04-14 papers/paper.tex
@@
 
-\textbf{EDITING POINT}
-
 Ultimately, modifiable syntax leads to better programming languages.
@@
 Since each programming language has its own compiler, there is some redundancy in each implementation. 
+Essentially, Glossa abstracts the parts of a compiler that don't depend on which language is being compiled, and reads in rules for each language.
+Because of this, Glossa allows simple implementations of programming languages, which means that Glossa can easily become capable of translating many different languages with ease.
 For example, the lexer for a C++ compiler and a Java compiler would be extremely similar, since both languages use braces, semicolons, and parentheses in the same way.
@@
 The string seperation function, however, is the same for every lexer, and would be redundant across multiple compilers.
-The same concept applies to Parsers and Generators, etc.. (Parsers read tokens and produce an ast, Generators use an AST to generate code)
+The same concept applies to Parsers and Generators, etc.. (Parsers read tokens and produce an AST, Generators use an AST to generate code)
 
 If programming languages could be compiled with a framework, this redundancy would go away, and programming language researchers would be able to focus on the language itself, as opposed to its compiler.
-Essentially, Glossa abstracts the parts of a compiler that don't depend on which language is being compiled, and reads in rules for each language, effectively seperating the language from how it is compiled.
-Because of this, Glossa allows simple implementations of programming languages, which means that Glossa can easily become capable of translating many different languages with ease.
 
@@
     \node (lfiles)  [io, right of=lrules, xshift=2cm]  {Lex Files};
-    \node (parser)  [process, below of=tokens]        {Parser};
+e   \node (parser)  [process, below of=tokens]        {Parser};
     \node (asta)    [io, below of=parser]             {AST};
@@
 
-Transformations to the AST allow for an overall simpler compilation process, reducing the number of construction files required for an output language. 
-AST transformations also solve non-isomorphisms, which is very useful if two languages are not very similar.
+AST Transformations solve non-isomorphisms, making language conversions more flexible by reducing language-to-language dependencies.
+Essentially, languages with a specialized feature set convert their language features to generalized ones (i.e.
+Haskell pattern matching might become a series of conditional checks on the arguments of a function).
+(Initial AST -\textgreater Universal AST)
+Then, if the output language does not contain some features in the Universal Feature Set, then it represents the same concept in its native form. (Universal AST -\textgreater Specialized AST).
 
-Essentially, transformations change language-specific features into more generalized ones. 
-AST transforms can also model code optimizations.
+For example: 
+Haskell's Pre-transformer might convert a parsed \textit{Data} element into a universal structure like a class.
+(Haskell's special data type is not in the Universal Feature set, but a class is.)
+Then, if the output is in a language that doesn't support classes, i.e.
+C, then C's Post-transformer would convert the class to struct-function-collections, creating the specialized AST, which would be compilable in C.
+
+\newpage
+\begin{tikzpicture}[node distance=2.5cm]
+
+    \node (asta)   [io]                       {AST};
+    \node (transa) [process, below of=asta]   {Pre-transformer};
+    \node (astb)   [io, below of=transa]       {Universal AST};
+    \node (transb) [process, below of=astb]   {Post-Transformer};
+    \node (astc)   [io, below of=transb]       {Specialized AST};
+
+    \draw [arrow] (asta)   -- (transa);
+    \draw [arrow] (transa) -- (astb);
+    \draw [arrow] (astb)   -- (transb);
+    \draw [arrow] (transb) -- (astc);
+
+    % title
+    \node[align=center,font=\bfseries, yshift=2em] (title) 
+	at (current bounding box.north)
+	{Dual-AST transform};
+
+\end{tikzpicture}
+\newpage
 
 Each element of the AST is MultiSymbol, which is a tag (string), and a string dictionary of symbols.
-To transform an AST element, the tag can be changed, or elements within the string dictionary can be manipulated.
+Each of these symbols can be either another MultiSymbol, or an atom like a literal, operator, or identifier.
+To transform an AST element, the tag can be changed, or elements within the dictionary can be manipulated.
 
@@
 \begin{verbatim}
-add    key (literal | identifier | ..) (2 | x | ...)
-append key (literal | identifier | ..) (2 | x | ...)
-copy   key1 key2
-move   key1 key2
-copy-append key1 key2
-move-append key1 key2
+createreg [name]
+// Copy an element from global multisymbol table to a key in a register's multisymbol table
+reg [name] transfer(-append) [reg-key] [global-key]
+// Move the multisymbol from a register to the destination key in the multisymbol table.
+If a destination_reg is specified, this table is the table of a register.
+Otherwise, it is the global multisymbol table
+pushback [reg-name] [destination] (optional)[destination_reg]
+// Prefix for performing an operation on a register
+reg [name] {command (any of below)}
+
+// The following also work with operations on the table of the current multisymbol
+// In add and append, type might be "identifier" or "literal" and value might be "x" or "2"
+// I.e to add an identifier foo under the key "name", use the command (add name identifier foo)
+// Add overwrites a key, append adds onto it.
+add    [key] [type] [value]
+append [key] [type] [value]
+// Move deletes the source key, copy does not.
+copy(-append) [key1] [key2]
+move(-append) [key1] [key2]
+// Change the tag of the register
 retag newtag
+// Delete a key from the multisymbol table
+delete [key]
 \end{verbatim}
@@
 
-If Glossa has adequate language descriptions, then translations are trivial. 
-Since Glossa can convert one language to another, it works as a pre-processor.
-Glossa has the ability for languages to inherit from and extend other languages, so, for example, C++ might inherit from C, and then implement class statements that compile into C code.
+Because Glossa dynamically reads in language descriptions, it can support a large number of programming languages.
+When given adequate description files, Glossa is potentially as capable as a specialized compiler or interpreter.
+Several examples of Glossa's translation capabilities are shown in the Appendix.
+
+Even though translation works very well, there are still several limitations to keep in mind:
+Retention of readability is not always garunteed, especially if there are many non-isomorphisms that need to be solved.
+Code that uses libraries is harder to translate: 
+It requires either a foreign function interface to be written, or the library to be translated alongside the software. 
+Translation of the library depends on access to the library's source code, which isn't always available.
 
@@
 Since Glossa uses dynamic language descriptions, languages can easily be created or modified by changing their descriptor files. 
+This functionality encourages language experimentation.
 Glossa also allows languages to inherit from existing languages. 
 For example, Glossa's descriptions for C++ might inherit from C, and only overwrite or add features.
-This functionality makes language experimentation painless, as code doesn't even need to be recompiled.
+
+Language design in Glossa is not affected in the same way that Translation is.
+The only possible limitation is the descriptor file interface.
+The success of an implemented language depends on how well it has been described.
+If description is straightforward, then language creation will be as well.
 
@@
 
-This example isn't necessarily meant to be an actual programming language, but more to show how a language could easily be implemented in Glossa.
+This is only an example of a DSL (Domain Specific Language), but a full language could easily be implemented using the exact same concepts.
 
@@
 While Glossa only supports a few different languages, it could easily support more if more description files were written.
-However, Glossa's interface would benefit from simplification, since writing description files is a hard task. Also, even in description files, there is some redundancy that could be eliminated.
+However, Glossa's interface would benefit from simplification, since writing description files is a hard task. 
+Also, even in description files, there is some redundancy that could be eliminated.
+As the description file interface improves, Glossa will come closer to being an idealistic multi-language source to source compiler.
 
-Glossa has accomplished far more than it originally set out to: Perhaps the software will mature in the future, and eventually be used at the industry level.
+While Glossa is useful at doing some automated translations, it is likely more useful for implementing new programming languages.
+Because of the generalizations (discarding of hard-coded rules) that Glossa makes, changing language definitions is trivial compared to the potential difficulty of modifying the source of a compiler.
+With Glossa, a new language can be implemented in a minimal amount of time, and then modified easily.
+
+Glossa has accomplished far more than it originally set out to: Perhaps as its interface improves, Glossa can be used as groundwork for an industrial-level compiler framework.
 

### 2017-04-23 papers/paper.tex
Adds FORTRAN functions/interfaces

@@
 // Copy an element from global multisymbol table to a key in a register's multisymbol table
-reg [name] transfer(-append) [reg-key] [global-key]
+transfer(-append) [reg-name] [global-key] [reg-key] 
 // Move the multisymbol from a register to the destination key in the multisymbol table.
@@
 Otherwise, it is the global multisymbol table
-pushback [reg-name] [destination] (optional)[destination_reg]
+pushback(-override) [reg-name] [destination] (optional)[destination_reg]
 // Prefix for performing an operation on a register

### 2017-04-23 examples/circle/main.f90

@@ -1,0 +1,52 @@
+!-----Area_Circle----------------------------------------------------
+!
+!  Function to compute the area of a circle of given radius
+!
+!---------------------------------------------------------------------
+
+FUNCTION Area_Circle(r)
+
+IMPLICIT NONE
+REAL :: Area_Circle
+REAL, INTENT(IN) :: r
+
+! Declare local constant Pi
+REAL, PARAMETER :: Pi = 3.1415927
+
+Area_Circle = Pi * r * r
+
+END FUNCTION Area_Circle
+
+PROGRAM Area
+!---------------------------------------------------------------------
+!
+!  This program computes the area of a circle given the input radius
+!
+!  Uses:  FUNCTION Area_Circle (r)
+!
+!---------------------------------------------------------------------
+IMPLICIT NONE
+
+INTERFACE 
+!   FUNCTION Area_Circle (r)
+!     REAL, Area_Circle
+!     REAL, INTENT(IN) :: r
+!   END FUNCTION Area_Circle
+END INTERFACE
+
+! Declare local variables
+REAL :: radius
+
+WRITE(*,*) "Calculating circle area"
+WRITE(*,*) Area_Circle(2)
+
+!  Prompt user for radius of circle
+!write(*, '(A)', ADVANCE = "NO") "Enter the radius of the circle:  "
+!read(*,*) radius
+
+! Write out area of circle using function call
+!write(*,100) "Area of circle with radius", radius, " is", &
+!            Area_Circle(radius)
+!100 format (A, 2x, F6.2, A, 2x, F11.2)
+
+END PROGRAM 

### 2017-04-23 src/gen/branch.hpp
Adds FORTRAN datatype parser

@@ -1,5 +1,4 @@
-#pragma once
-
+#pragma once 
 #include "../tools/tools.hpp"
 #include "../lex/seperate.hpp"
 #include "../lex/lexmap.hpp"

### 2017-04-26 papers/paper.tex
WIP

@@
 Glossa is both a multi-language source to source compiler and, by extension, a framework for creating compilers.
-Glossa's main goal is to convert any programming language \textbf{A} to any programming language \textbf{B}, such that the output in \textbf{B} is indistinguishable from code written by a native \textbf{B} programmer, in the same way that the output from Google Translate would ideally look as if it were written by a native speaker.
+Glossa should convert any programming language \textbf{A} to any programming language \textbf{B}, such that the output in \textbf{B} is indistinguishable from code written by a native \textbf{B} programmer, in the same way that the output from Google Translate would ideally look as if it were written by a native speaker.
 If given an adequate description of each language's grammar, one language can be converted to another if the languages are \textit{isomorphic}.
 If two languages are not \textit{isomorphic}, one can still be converted to another if the non-isomorphisms are solved through an AST transformation.
-For example, C++ can be converted to C if classes are represented as collections of functions that all take a struct as their first argument.
-(Since C++ supports classes, but C does not (an example of a non-isomorphism).)
-However, solving non-isomorphisms through AST transformations potentially compromises output code readability.
-This being noted, a human making the conversion would also have to compromise readability, since there \textit{is no other way to retain functionality.} So, when it has to, Glossa compromises output code readability for proper functionality.
 
-Glossa has several caveats. 
-Grammars need to be described fully to Glossa, which is potentially difficult.
-The more accurate a grammar description becomes, the more complicated it is to create.
-However, grammar files must be simple, so that they can be created/understood/modified by users.
-Also, the more non-isomorphisms that exist between two programming languages, the less readable the result of a conversion between them will be.
-This being noted, accurate conversions are 100\% possible if the description files are written properly.
-For description files to be easily written, their syntax should be as intuitive as possible. 
-In Glossa, the description file formats have been refactored several times, so that the current descriptor file syntax is near optimal.
-
-Glossa accomplishes near 100\% conversions for Python3 to C++, as well as Python2 to Python3.
-Glossa has proof of concept conversions for FORTRAN to C++, FORTRAN to Python3, and proof of concept for implementation of a new programming language, Auta.
-While the software is still in its infancy, the core concepts have been proven, indicating that an industry level multi-language source to source compiler is possible.
+Additionally, Glossa should provide a famework for creating programming languages.
+This is done using the translation interface, where syntax of a new language is described with files, and the language is translated either to machine code, or another programming language which will later be compiled.
 
@@
 % ==================================================
-
-Since Glossa aims to be capable of translating many different programming languages, it must provide a dynamic framework for easily modifying syntax of input and output languages. 
+`
+Since Glossa was created to be capable of translating many different programming languages, it must provide a dynamic framework for easily modifying syntax of input and output languages. 
 In addition to letting Glossa translate existing languages, this functionality makes implementing new programming languages very simple.
@@
 Assuming conversion from \textbf{A} to \textbf{B}, as in the Abstract, Glossa creates the Lexer, Parser, and Transformer based on \textbf{A}, and the Generator based on \textbf{B}.
-As one would expect, this means that Glossa has four types of descriptor files:
+As one would expect, this means that Glossa uses four types of descriptor files:
 
 \begin{enumerate}
-    \item \textit{lex files}: A list of strings that constitute atomic types like string literals, operators, keywords 
+    \item \textit{lex files}: A list of strings that constitute atomic types like string literals, operators, keywords in language \textbf{A} 
     \item \textit{grammar files}: A description of a parser for each grammar element in language \textbf{A} 
@@
 
-Lex files are the most straightforward of all of Glossa's descriptor files.
+Lex files are the most straightforward of all of the descriptor files in Glossa.
 
@@
 
-Glossa's parse operation converts a list of tokens to an AST.
+Parsing converts a list of tokens to an AST.
 
-Glossa will attempt to identify remaining tokens with high-level statement types, which in turn use lower-level grammar types:
+Parsing will attempt to identify remaining tokens with high-level statement types, which in turn use lower-level grammar types:
 \begin{verbatim}
@@
 \end{lstlisting}
-might become
+will generate
 \lstset{language=c++}
@@
 Constructor files must define which values will be put into the namespace, so our full constructor file would start with:
-\begin{verbatim}
-defines
-lval
-\end{verbatim}
 Additionally, c++ has both header and source files in generation, but assignment statements look the same for each.
@@
 
-Because Glossa dynamically reads in language descriptions, it can support a large number of programming languages.
+Because Glossa dynamically reads in language descriptions, it can support a large number of programming languages both as inputs and outputs.
 When given adequate description files, Glossa is potentially as capable as a specialized compiler or interpreter.
-Several examples of Glossa's translation capabilities are shown in the Appendix.
+Several examples of translations done with Glossa are shown in the Appendix.
 
 Even though translation works very well, there are still several limitations to keep in mind:
-Retention of readability is not always garunteed, especially if there are many non-isomorphisms that need to be solved.
+Retention of readability is not always guaranteed, especially if there are many non-isomorphisms that need to be solved.
 Code that uses libraries is harder to translate: 
@@
 Glossa also allows languages to inherit from existing languages. 
-For example, Glossa's descriptions for C++ might inherit from C, and only overwrite or add features.
+For example, descriptions for C++ might inherit from C, and only overwrite or add features.
 
@@
 
-Recall the current suite of translation examples:
+Glossa currently ships with the following translation examples:
 \begin{enumerate}
@@
 
-Glossa's support for the different versions of Python and C++ output are significantly developed, supporting 80-90\% of the syntax for each language. 
+Support for the different versions of Python and C++ output are significantly developed, supporting 80-90\% of the syntax for each language. 
 However, support for FORTRAN is more experimental, but 100\% support would be trivial to add, since FORTRAN has very simple syntax.
@@
 Also, even in description files, there is some redundancy that could be eliminated.
-As the description file interface improves, Glossa will come closer to being an idealistic multi-language source to source compiler.
+As the description file interface improves, Glossa will come closer to being an ideal multi-language source to source compiler.
 

### 2017-04-26 papers/paper.tex
Adds final paper draft

@@
 Glossa is both a multi-language source to source compiler and, by extension, a framework for creating compilers.
-Glossa should convert any programming language \textbf{A} to any programming language \textbf{B}, such that the output in \textbf{B} is indistinguishable from code written by a native \textbf{B} programmer, in the same way that the output from Google Translate would ideally look as if it were written by a native speaker.
+Ideally, Glossa converts any programming language \textbf{A} to any programming language \textbf{B}, such that the output in \textbf{B} is indistinguishable from code written by a native \textbf{B} programmer, in the same way that the output from Google Translate would ideally look as if it were written by a native speaker.
 If given an adequate description of each language's grammar, one language can be converted to another if the languages are \textit{isomorphic}.
@@
 % ==================================================
-`
-Since Glossa was created to be capable of translating many different programming languages, it must provide a dynamic framework for easily modifying syntax of input and output languages. 
+
+Many codebases have become unmanagable: they either use two many programming languages, or outdated programming languages, making them obsolete.
+Modern software needs to be written in a modern language. However, code should not be ported by hand, as this wastes the developers time, which could be spent on more important tasks.
+
+Glossa translates any programming language to any other programming language.
+Since Glossa was created to be capable of translating many different programming languages, it provides a dynamic framework for easily modifying syntax of input and output languages. 
 In addition to letting Glossa translate existing languages, this functionality makes implementing new programming languages very simple.
@@
 Ultimately, modifiable syntax leads to better programming languages.
-As programming paradigms shift, so does syntax. 
+Programming paradigms are implemented in syntax, and paradigms determine code. 
+For example, strong, statically typed languages are used to build robust, scalable back-end software.
+Fluid, dynamically typed languages are used in scripting and front-end development.
+
 If a language can be changed quickly and easily, then different styles can easily be experimented with, improving the chance of finding an optimal style.
@@
 \begin{enumerate}
-    \item \textit{lex files}: A list of strings that constitute atomic types like string literals, operators, keywords in language \textbf{A} 
+    \item \textit{lex files}: A list of strings that constitute atomic types like string literals, operators, and keywords in language \textbf{A} 
     \item \textit{grammar files}: A description of a parser for each grammar element in language \textbf{A} 
@@
 
+\newpage
+
 \subsection{Lex Files}
@@
 \begin{verbatim}
-comment_delimiters  logicaloperators  operators  punctuators  string_delimiters  whitespace
+comment_delimiters  logicaloperators  operators  
+punctuators  string_delimiters  whitespace
 \end{verbatim}
@@
 \end{verbatim}
-Where "false" says if a whitespace element should be kept as a token when the language is lexed.
+Where each line is the name of a whitespace element, and a boolean indicating if the token should be kept when the language is lexed.
 
@@
 \end{tikzpicture}
+
 \newpage
@@
 // Move the multisymbol from a register to the destination key in the multisymbol table. 
-If a destination_reg is specified, this table is the table of a register.
-Otherwise, it is the global multisymbol table
+// If a destination_reg is specified, this table is the table of a register. 
+// Otherwise, it is the global multisymbol table
 pushback(-override) [reg-name] [destination] (optional)[destination_reg]
@@
 // The following also work with operations on the table of the current multisymbol
-// In add and append, type might be "identifier" or "literal" and value might be "x" or "2"
-// I.e to add an identifier foo under the key "name", use the command (add name identifier foo)
+// In add and append, type might be "identifier" or "literal" 
+//                              and value might be "x" or "2"
+// I.e to add an identifier foo under the key "name", 
+//   use the command (add name identifier foo)
 // Add overwrites a key, append adds onto it.
@@
 (This AST transform renames the syntax element to f, saving the old name to the key "old\_identifier"
+
+\subsection{Inheritance Lists}
+
+Languages can inherit from other programming languages.
+Currently, only the Parser for a particular language is inherited.
+Inheritance is defined in a special file, ./languages/lang\_name/inherits, which is simply a list of language IDs to inherit from.
+As with class constructs in programming, it is safer to only inherit from a single parent.
+However, heirarchical inheritance is possible.
+For example, Auta inherits from Python3, which inherits from Python\_core.
 
@@
 If description is straightforward, then language creation will be as well.
+
+Since Glossa ships with constructor files (Currently for Python3 and C++), a new language only has to provide grammar, lex and (optional) transformer files.
+
+For example, adding a function to a particular programming language takes a single line:
+\begin{verbatim}
+function: 'def' `@name identifier **` '(' `@args sep ',' identifier **` ')' ':' `@body *statement` 'end'
+\end{verbatim}
+To change this Python style function to one in Haskell:
+\begin{verbatim}
+function: `@name identifier **` `@args sep SPACE identifier **` '=' `@body return` 'end'
+\end{verbatim}
+Since these two parsers define the same fields (name, args, body), they would be compiled in identical ways.
+
+For reference, the CPython interpreter uses a Python grammar file, which is around 130 lines (counting whitespace).
+A grammar file for a similar language would be a similar size.
+While each line requires some careful thought, a new programming language could be implemented in a matter of hours.
+Alternatively, an existing language could be modified in the same way that the above function syntax was changed from Python style to Haskell style.
 
@@
 This is only an example of a DSL (Domain Specific Language), but a full language could easily be implemented using the exact same concepts.
+Autas grammar file is extremely brief (as it inherits syntax from Python3):
+
+\begin{verbatim}
+statement: `@val every`
+every: 'every' `@count optional literal int` `@unit identifier **` ':' `@body *statement` 'end'
+\end{verbatim}
+
+Most of Auta's functionality is made possible by a 200 line Python library, which is imported by the output script.
+While Auta is only a proof of concept, it was implemented in less than two hours, the majority of which was spent building the library.
 
@@
 
-Glossa has accomplished far more than it originally set out to: Perhaps as its interface improves, Glossa can be used as groundwork for an industrial-level compiler framework.
+Glossa has accomplished far more than it originally set out to.
+As it matures, it will certainly be capable of doing industrial-level transformations, as well as implementing new programming languages with minimal effort.
 

### 2019-09-07 papers/paper.tex
Fixes an ancient typo

@@
 
-Additionally, Glossa should provide a famework for creating programming languages.
+Additionally, Glossa should provide a framework for creating programming languages.
 This is done using the translation interface, where syntax of a new language is described with files, and the language is translated either to machine code, or another programming language which will later be compiled.
@@
 
-assignment: `@lval identifier **` `@op '='` `@rval boolexpression | expression`
+assignment: `@lval identifier **` \
+`@op '='` `@rval boolexpression | expression`
 \end{verbatim}
@@
 createreg [name]
-// Copy an element from global multisymbol table to a key in a register's multisymbol table
+// Copy an element from global multisymbol table to a 
+//key in a register's multisymbol table
 transfer(-append) [reg-name] [global-key] [reg-key] 
-// Move the multisymbol from a register to the destination key in the multisymbol table. 
-// If a destination_reg is specified, this table is the table of a register. 
+// Move the multisymbol from a register to the destination 
+// key in the multisymbol table. 
+// If a destination_reg is \
+// specified, this table is the table of a register. 
 // Otherwise, it is the global multisymbol table
@@
 
-// The following also work with operations on the table of the current multisymbol
+// The following also work with operations on the 
+// table of the current multisymbol
 // In add and append, type might be "identifier" or "literal" 
@@
 \begin{verbatim}
-function: 'def' `@name identifier **` '(' `@args sep ',' identifier **` ')' ':' `@body *statement` 'end'
+function: 'def' `@name identifier **` '(' `@args sep ',' \
+identifier **` ')' ':' `@body *statement` 'end'
 \end{verbatim}
@@
 \begin{verbatim}
-function: `@name identifier **` `@args sep SPACE identifier **` '=' `@body return` 'end'
+function: `@name identifier **` \
+`@args sep SPACE identifier **` '=' `@body return` 'end'
 \end{verbatim}
